\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Sweet and Saltines •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Saltine crackers \dotfill 2-3 sleeves \\
    Kerrygold butter \dotfill 2 sticks (1 cup) \\
    Light brown sugar \dotfill 1 cup \\
    Lindt milk chocolate bars \dotfill 8 oz\\
    Crushed nuts or pretzels \dotfill \nicefrac{1}{4} cup \\
    Cooking spray \dotfill as needed
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{425°F} ---
Line a large cookie sheet with foil and \textbf{cooking spray} ---
Prepare a second large cookie sheet with crushed ice ---
Crush \textbf{nuts} and/or \textbf{pretzels}; set aside in \textit{Small Bowl~\#1} ---
Break apart \textbf{chocolate bars} into 1~inch pieces; set aside in \textit{Medium Bowl~\#1} ---
Have a candy thermometer ready

\begin{enumerate}
    \item Arrange \textbf{saltine crackers} in a single layer, salt side down, on the prepared sheet.
    \item In a medium saucepan, combine 2~sticks (1~cup) \textbf{butter} and 1~cup \textbf{brown sugar}.
    \item Heat the mixture over medium heat, stirring constantly until the \textbf{butter} is completely melted and the \textbf{sugar} is dissolved.
    \item Once the mixture starts to bubble, stop stirring and let it cook undisturbed. Cook until it reaches \textit{285°F} (soft-crack stage) on a candy thermometer, about \textit{3-5~minutes}. Watch for visual cues: the caramel should be a deep golden brown color and have a smooth, glossy appearance. You may see wisps of smoke starting to form.
    \item Immediately remove from heat and pour evenly over the arranged \textbf{crackers}. Work quickly as the caramel will start to set.
    \item Bake for \textit{3-5~minutes} until the caramel is bubbly all over. Watch carefully.
    \item Remove from oven and quickly arrange \textbf{chocolate} (\textit{Medium Bowl~\#1}) over the top.
    \item Wait about \textit{1~minute}, then spread the melted \textbf{chocolate} evenly.
    \item Sprinkle crushed \textbf{nuts} and/or \textbf{pretzels} (\nicefrac{1}{4}~cup, \textit{Small Bowl~\#1}) over the melted \textbf{chocolate}.
    \item To cool quickly, place the hot cookie sheet with the crackers on top of the ice-filled sheet. For faster setting, place in the freezer if possible.
    \item Once cold but not frozen, break into pieces.
    \item Store in an airtight container.
\end{enumerate}

\end{document}
