\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\widowpenalty=10000
\clubpenalty=10000
\interlinepenalty=500

\title{Chicken, Mushroom \& Spinach Pasties}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{quote}
\textit{A gluten-free butter pastry (Bob's Red Mill 1-to-1 flour) encloses a creamy filling of seared chicken thighs, browned cremini mushrooms, shallots, and spinach bound by a roux-based sauce with white wine, thyme, tarragon, Gruyère, and cream cheese. Pasties are crimped, vented, and baked until deeply golden. Serve with Shallot--Dijon Cream Sauce (separate recipe). Makes 8 meal-size pasties.}
\end{quote}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Bob's Red Mill 1-to-1 GF flour \dotfill 4 cups (500~g) \\
    Salt \dotfill 2 tsp. (pastry); to taste (filling) \\
    Unsalted butter, cold, cubed \dotfill 21 Tbsp. (300~g) \\
    Egg yolk, large \dotfill 1 \\
    Ice water \dotfill 10--12 Tbsp. \\
    Chicken thighs, boneless skinless \dotfill 1\nicefrac{1}{2}--2~lb. \\
    Cremini mushrooms \dotfill 1~lb. \\
    Shallots, medium \dotfill 2--3 \\
    Garlic cloves \dotfill 4--6 \\
    Unsalted butter \dotfill 6 Tbsp. \\
    Dry white wine \dotfill \nicefrac{1}{4} cup \\
    All-purpose flour \dotfill 6 Tbsp. \\
    Chicken stock \dotfill 1\nicefrac{1}{2} cups \\
    \columnbreak
    Heavy cream \dotfill \nicefrac{1}{2} cup \\
    Nutmeg \dotfill pinch \\
    Cream cheese \dotfill 4 oz. \\
    Gruyère, grated \dotfill 4 oz. \\
    Frozen spinach \dotfill 10 oz. \\
    Thyme, dried \dotfill 2 tsp. \\
    Tarragon, dried \dotfill 2 tsp. \\
    Dijon mustard \dotfill 1--2 tsp. \\
    Lemon \dotfill 1 (zest only) \\
    Black pepper, freshly ground \dotfill to taste \\
    Egg, for wash \dotfill 1 \\
    Water (for egg wash) \dotfill 1 Tbsp.
\end{multicols}

\section*{Directions}

\noindent
Chill \textbf{butter} for pastry until very cold (freeze \textit{15--20~minutes} if needed) ---
Dice \textbf{shallots} and mince \textbf{garlic}; combine in \textit{Small Bowl~\#1} (aromatics) ---
Combine 2~tsp. \textbf{thyme} and 2~tsp. \textbf{tarragon} in \textit{Small Bowl~\#2} (herbs) ---
Zest \textbf{lemon} and combine with 1--2~tsp. \textbf{Dijon} in \textit{Small Bowl~\#3} (finish) ---
Thaw \textbf{spinach}, wring in a clean towel until bone-dry; set aside ---
Quarter \textbf{mushrooms}; have \textbf{chicken stock}, \textbf{cream}, and \textbf{wine} measured and nearby ---
Preheat oven to \textit{375°F} before assembly

\begin{enumerate}
    \item Make the pastry: In a food processor, pulse 4~cups \textbf{GF flour} and 2~tsp. \textbf{salt} to combine. Add 21~Tbsp. cold cubed \textbf{butter} and pulse until pieces are pea-sized and mixture looks like coarse meal, \textit{8--12 pulses}. Do not overmix. In a small bowl, whisk 1 \textbf{egg yolk} with 10--12~Tbsp. \textbf{ice water}. With processor running, add liquid in a thin stream and pulse until dough just holds together when squeezed (shaggy, not smooth); you may not need all the water. Turn dough out onto a work surface, gather gently, and divide into 8 equal portions. Form each into a disc, wrap individually in plastic wrap, and refrigerate for \textit{2--3~hours} (or overnight). Dough must be cold for rolling.

    \item Cook the chicken: Season 1\nicefrac{1}{2}--2~lb. \textbf{chicken thighs} with \textbf{salt} and \textbf{pepper}. In a large skillet over \textit{medium-high heat}, sear in one or two batches until golden and cooked through, \textit{4--6~minutes per side}. Chicken is done when internal temperature reaches \textit{165°F} and juices run clear. Transfer to a plate; when cool enough to handle, dice into \textit{\nicefrac{1}{2}-inch} pieces and place in \textit{Medium Bowl~\#1}. Set aside.

    \item Cook the mushrooms: In the same skillet over \textit{medium-high heat}, cook \textbf{mushrooms} in one or two batches (do not crowd) until deeply browned and all liquid has evaporated, \textit{10--12~minutes}. Stir occasionally; mushrooms are done when the pan is dry, mushrooms are dark golden, and they smell nutty. Transfer to \textit{Medium Bowl~\#2} and set aside.

    \item Build the sauce: In the same skillet over \textit{medium} or \textit{medium-low heat}, melt 6~Tbsp. \textbf{butter}. Add \textbf{shallots} and \textbf{garlic} (\textit{Small Bowl~\#1}) and cook, stirring occasionally, until shallots are soft and translucent with no raw bite, \textit{6--8~minutes}. Do not brown. Add \nicefrac{1}{4}~cup \textbf{dry white wine}, scrape up any browned bits, and simmer until reduced by half, \textit{2--3~minutes}.

    \item Sprinkle 6~Tbsp. \textbf{flour} over the shallot mixture and cook, stirring constantly, for \textit{2~minutes} until roux smells nutty and no raw flour remains. Gradually whisk in 1\nicefrac{1}{2}~cups \textbf{chicken stock}, then \nicefrac{1}{2}~cup \textbf{heavy cream}, adding liquid in a steady stream to prevent lumps. Add a pinch of \textbf{nutmeg}. Bring to a gentle simmer and cook, stirring often, until sauce is very thick and coats the back of a spoon heavily (a line drawn through it with your finger should hold clearly), \textit{5--7~minutes}. Sauce must be thick enough that the filling will not leak when enclosed.

    \item Remove skillet from heat. Stir in 4~oz. \textbf{cream cheese} until melted and smooth, then 4~oz. grated \textbf{Gruyère} until melted. Fold in \textbf{chicken} (\textit{Medium Bowl~\#1}), \textbf{mushrooms} (\textit{Medium Bowl~\#2}), wrung-dry \textbf{spinach}, \textbf{thyme} and \textbf{tarragon} (\textit{Small Bowl~\#2}), and \textbf{lemon zest} and \textbf{Dijon} (\textit{Small Bowl~\#3}). Season with \textbf{salt} and \textbf{pepper}. Taste and adjust---filling should be slightly over-seasoned (flavors mellow when baked). Spread filling in an even layer on a rimmed sheet pan and refrigerate until completely cold, \textit{1--2~hours} (or overnight). Cold filling is critical to avoid soggy pastry.

    \item Assemble the pasties: Line one or two large baking sheets with parchment. Beat 1 \textbf{egg} with 1~Tbsp. \textbf{water} in a small bowl for egg wash. Working with one dough disc at a time (keep others chilled), roll between two sheets of parchment to a \textit{\nicefrac{1}{8}-inch} thick circle about \textit{6--7~inches} in diameter. Place \textit{\nicefrac{3}{4}~cup} cold \textbf{filling} slightly off-center on one half. Brush pastry edges with \textbf{egg wash}, fold the other half over to form a half-moon, and press edges to seal. Crimp the edge in a rope crimp (fold and pinch along the seam). Place on prepared sheet. Repeat for remaining 7 pasties. Brush tops of all pasties with \textbf{egg wash} and cut 2--3 small steam vents in each.

    \item Bake at \textit{375°F} for \textit{30--35~minutes} until pastry is deeply golden and firm, and filling reaches \textit{165°F} in the center. Pasties are done when the crust is golden brown and no longer soft, and an instant-read thermometer inserted into the center of the filling reads \textit{165°F}. Cool \textit{5--10~minutes} before serving---filling is very hot. Serve with Shallot--Dijon Cream Sauce (separate recipe).
\end{enumerate}

\newpage

\section*{Equipment Required}
\begin{itemize}
    \item Food processor
    \item Large skillet (12-inch preferred)
    \item Rimmed baking sheet(s) (one or two, for cooling filling and baking pasties)
    \item Rolling pin
    \item Parchment paper
    \item Round cutter or plate, 6--7~inches diameter
    \item Pastry brush
    \item Instant-read thermometer
    \item Small prep bowls (3)
    \item Medium prep bowls (2)
    \item Measuring cups and spoons
    \item Cutting board and chef's knife
    \item Clean kitchen towel (for wringing spinach)
\end{itemize}

\section*{Hints and Notes}

\subsection*{Yield}
\begin{itemize}
    \item Makes 8 meal-size pasties (6--7~inch diameter)
    \item Serves 8 as a main dish
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item \textit{Small Bowl~\#1} --- aromatics: diced \textbf{shallots}, minced \textbf{garlic}
    \item \textit{Small Bowl~\#2} --- 2~tsp. \textbf{thyme}, 2~tsp. \textbf{tarragon}
    \item \textit{Small Bowl~\#3} --- \textbf{lemon zest}, 1--2~tsp. \textbf{Dijon}
    \item \textit{Medium Bowl~\#1} --- cooked diced \textbf{chicken} (set aside after step 2)
    \item \textit{Medium Bowl~\#2} --- cooked \textbf{mushrooms} (set aside after step 3)
    \item Wring \textbf{spinach} bone-dry before adding to filling; excess moisture will thin the sauce and risk soggy pastry
    \item Keep pastry \textbf{butter} very cold (almost frozen) and chill dough \textit{2--3~hours} before rolling
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use \textbf{Bob's Red Mill 1-to-1 GF flour} as specified; other blends are not validated for this pastry ratio
    \item \textbf{Cremini} mushrooms give the best depth; cook until all liquid is gone so the filling stays thick
    \item \textbf{Dry white wine} (e.g., Pinot Grigio, Sauvignon Blanc) for deglazing; avoid ``cooking wine''
    \item \textbf{Gruyère} and \textbf{cream cheese} add body and tang; grate Gruyère just before use for best melt
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Pastry: minimal handling---pulse only until dough comes together; overworking makes GF pastry crumbly. Roll between parchment to avoid sticking and tearing.
    \item Mushrooms must be cooked until the pan is completely dry (no liquid); this takes \textit{10--12~minutes} and is critical for a thick, non-leaky filling.
    \item Filling must be completely cold before assembly; hot filling softens the pastry and causes leaks.
    \item Do not overfill---\textit{\nicefrac{3}{4}~cup} per pastie maximum. Seal edges well and crimp firmly; cut vents so steam can escape.
    \item Bake until deeply golden; internal \textit{165°F} ensures food safety and a hot, set filling.
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Pastry dough: refrigerate \textit{3~days} or freeze \textit{3~months}; thaw overnight in refrigerator
    \item Filling: refrigerate \textit{3~days}; must be cold before assembling
    \item Assembled unbaked pasties: refrigerate \textit{1~day} or freeze \textit{3~months}; from frozen, add \textit{10--15~minutes} to baking time
    \item Baked pasties: refrigerate \textit{3--4~days} or freeze \textit{2~months}; reheat at \textit{350°F} for \textit{15--20~minutes} until internal \textit{165°F}
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve with \textbf{Shallot--Dijon Cream Sauce} (separate recipe) for dipping or drizzling
    \item Pasties are best within \textit{5--10~minutes} of cooling from the oven; reheat leftovers until filling reaches \textit{165°F}
\end{itemize}

\end{document}
