\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Easy Freezer Breakfast Burritos}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{quote}
\small
\begin{em}
Easy Freezer Breakfast Burritos offer a delicious and convenient way to enjoy a hearty breakfast. Perfect for meal prep, these burritos feature a flavorful blend of sausage, eggs, cheese, and tater tots, all wrapped in a soft flour tortilla.
\end{em}
\end{quote}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Breakfast sausage \dotfill 16-24 oz. \\
    Bell peppers,  \dotfill 1 cup \\
    Onion, small diced \dotfill ½ cup \\
    Large eggs \dotfill 10 \\
    Milk \dotfill 1 ½ cups \\
    \columnbreak
    Sour cream \dotfill ¾ cup \\
    Salt \dotfill 1 tsp. \\
    Black pepper \dotfill ¼ tsp. \\
    Frozen tater tots \dotfill 30 oz. \\
    Flour tortillas, burrito size \dotfill 12-15 \\
    Shredded cheese \dotfill 3-4 cups
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to 350F --- Dice \textbf{bell peppers} and \textbf{onions}

\begin{enumerate}
    \item Cook the \textbf{breakfast sausage}, \textbf{bell peppers,} and \textbf{onions} over medium heat, crumbling the sausage until cooked through. Drain grease.
    \item Whisk together the \textbf{eggs}, \textbf{milk},\textbf{ sour cream}, \textbf{salt}, and \textbf{black pepper} until smooth.
    \item Lightly grease a 9" x 13" baking pan. Place the \textbf{tater tots} in the bottom of the pan.
    \item Sprinkle the sausage mixture over the \textbf{tater tots} in the prepared pan. Pour the egg mixture evenly over the top. 
    \item Bake at 350F for 30 minutes covered, then 25-45 minutes uncovered until set.
    \item If freezing, let the casserole cool to room temperature. Scoop about 1/2 cup of the casserole onto each \textbf{tortilla}, sprinkle with \textbf{cheese}, fold the sides, and roll up into a burrito.
    \item To freeze, place cooled burritos in a freezer bag. Reheat in the microwave or oven as desired.
\end{enumerate}

\end{document}
