\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Easy Breakfast Burritos}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{quote}
\small
\begin{em}
These Easy Breakfast Burritos are perfect for busy mornings, combining classic breakfast flavors in a convenient handheld meal. They can be prepped quickly and are freezable for grab-and-go breakfasts, requiring just two minutes in the microwave to reheat.
\end{em}
\end{quote}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Vegetable oil \dotfill 3 tbsp \\
    Hash brown potatoes \dotfill 4 cups \\
    Breakfast sausage, \dotfill 1 lb. \\
    Eggs \dotfill 8 \\
    \columnbreak
    Chopped Green Chiles \dotfill 1 can \\
    Pepper \dotfill ½ tsp \\
    Salt \dotfill ½ tsp \\
	Cheddar and/or  Jack Cheese \dotfill 2 cups \\
    Flour tortillas \dotfill 12 \\
\end{multicols}

\section*{Directions}

\begin{enumerate}
    \item Heat 2 tablespoons \textbf{oil} in a nonstick skillet. Add \textbf{hash browns}, press down lightly, and cook without moving for 7 minutes. Drizzle with remaining \textbf{oil}, turn, and cook until browned and hot.
    \item Beat \textbf{eggs}, \textbf{green chiles}, \textbf{salt}, and \textbf{pepper} in a bowl. Cook \textbf{sausage} in the skillet until browned, then stir in \textbf{egg} mixture and cook until scrambled.
    \item To assemble burritos, spoon a line of \textbf{hash browns} down the center of each \textbf{tortilla}. Top with \textbf{cheese} and \textbf{egg} mixture.
    \item Roll up each \textbf{tortilla} tightly to secure the filling. Serve immediately, or follow freezing instructions.
    \item To freeze, wrap each burrito in foil and store in a freezer bag for up to 1 month. To reheat, wrap in a damp paper towel and microwave until heated through.
\end{enumerate}

\end{document}
