\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Cheesy Bacon Hash Brown Casserole}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Frozen hash browns, thawed \dotfill 30 oz. \\
    Cream of chicken soup \dotfill 10.5 oz. can \\
    Sour cream \dotfill 1¾ cups \\
    Butter, melted \dotfill ½ cup \\
    Onion, diced \dotfill ¾ cup \\
    Sharp cheddar cheese \dotfill 2 cups \\
    Gruyère cheese \dotfill 1 cup \\
	\columnbreak
    Bacon, cooked \& crumbled \dotfill 1 lb. \\
    Sliced mushrooms, chopped \dotfill 8 oz. can \\
    Sun-dried tomatoes, chopped \dotfill ½ cup \\
    Garlic powder \dotfill 1 tsp. \\
    Onion powder \dotfill 1 tsp. \\
    Black pepper \dotfill ½ tsp. \\
    Cayenne pepper \textit{(optional)} \dotfill ¼ tsp. \\
    Potato chips, crushed \dotfill 2 cups \\
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textbf{350°F} (175°C) ---
Grease a 9x13 inch baking dish ---
Thaw and pat dry \textbf{hash browns} ---
Dice \textbf{onion} ---
Shred \textbf{cheddar} and \textbf{Gruyère} cheese ---
Cook and crumble \textbf{bacon} ---
Drain and chop \textbf{mushrooms} ---
Crush \textbf{potato chips}

\begin{enumerate}
    \item Rehydrate \textbf{sun-dried tomatoes} in hot water for 10 minutes, then drain and chop.
    \item In a large bowl, mix \textbf{hash browns}, \textbf{cream of chicken soup}, \textbf{sour cream}, melted \textbf{butter}, diced \textbf{onion}, 1½ cups \textbf{cheddar cheese}, \textbf{Gruyère cheese}, ¾ of the crumbled \textbf{bacon}, chopped \textbf{mushrooms}, chopped \textbf{sun-dried tomatoes}, \textbf{garlic powder}, \textbf{onion powder}, \textbf{black pepper}, and \textbf{cayenne pepper} (if using).
    \item Spread the mixture evenly in the prepared baking dish.
    \item Top with remaining ½ cup \textbf{cheddar cheese} and crushed \textbf{potato chips}.
    \item Bake for 50-55 minutes until golden brown and bubbly.
    \item Remove from oven and sprinkle remaining \textbf{bacon} on top.
    \item Let cool for 5-10 minutes before serving.
\end{enumerate}

\end{document}
