\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Lime and Cilantro Rice}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{quote}
\small
\begin{em}
This Chuy's-inspired Lime and Cilantro Rice is a fragrant and flavorful side dish that perfectly complements Mexican and Tex-Mex cuisine. The bright citrus notes and fresh herbs elevate simple white rice to a restaurant-quality accompaniment for your favorite meals.
\end{em}
\end{quote}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Long-grain white rice \dotfill 2 cups \\
    Chicken broth \dotfill 3 cups \\
    Olive oil \dotfill 2 Tbsp. \\
    Onion, small \dotfill 1 \\
    Garlic cloves \dotfill 3 \\
    Salt \dotfill 1 tsp. \\
    \columnbreak
    Lime juice, fresh \dotfill ¼ cup \\
    Lime zest \dotfill 1 lime \\
    Cilantro, fresh \dotfill ½ cup \\
    Butter \dotfill 2 Tbsp. \\
    Jalapeño (optional) \dotfill 1 Tbsp. \\
\end{multicols}

\section*{Directions}

\noindent
Rinse \textbf{rice} until water runs clear ---
Finely dice \textbf{onion} ---
Mince \textbf{garlic} ---
Zest and juice \textbf{limes} ---
Finely chop \textbf{cilantro} ---
If using, finely dice \textbf{jalapeño}

\begin{enumerate}
    \item Heat \textbf{olive oil} in a medium saucepan over medium heat. Sauté \textbf{onion} for 2-3 minutes until translucent.
    \item Add \textbf{garlic} (and optional \textbf{jalapeño}) and cook for 30 seconds until fragrant.
    \item Add rinsed \textbf{rice} to the pan and stir to coat with oil. Toast for about 2 minutes, stirring frequently.
    \item Transfer rice mixture to rice cooker. Add \textbf{chicken broth} to appropriate fill line. Stir gently to combine.
    \item Close lid and cook on standard white rice setting until cycle is complete.
    \item Once done, let rice sit for an additional 5-10 minutes with the lid closed.
    \item Open lid and fluff rice with a fork. Add \textbf{lime juice}, \textbf{lime zest}, chopped \textbf{cilantro}, and \textbf{butter}. Fold gently until well combined and butter is melted.
    \item Taste and adjust seasoning if needed, salt, lime juice, or cilantro to preference.
\end{enumerate}

\end{document}