\documentclass[11pt,letterpaper]{article}
\usepackage[left=1.5in,right=1.5in,top=1in,bottom=1in]{geometry}
\usepackage{fontspec}
\usepackage{multicol}

\setmainfont[Scale=1.3]{Doves Type}

\title{Hungarian Mushroom Soup}
\author{
  AllRecipes.com (with modifications) \\
  \small{ https://www.allrecipes.com/recipe/17897/hungarian-mushroom-soup/ }
}
\date{\today}

\begin{document}
\maketitle

\section*{Ingredients}
\begin{multicols}{2}
    \begin{itemize}
        \item 8 Tbsp. unsalted butter
        \item 4 cups onions chopped \\ (two medium onions)
        \item 2 lbs. mushrooms sliced
        \item 6 cups chicken broth
        \item 2 Tbsp. soy sauce
        \item 1 tsp. Hungarian hot paprika
        \item 4 tsp. Hungarian sweet paprika
        \item 4 tsp. dried dill weed
    \end{itemize}
    \columnbreak
    \begin{itemize}
        \item 2 cups milk
        \item 6 Tbsp. all-purpose flour
        \item 1 cup sour cream
        \item ½ cup fresh parsley chopped 
        \item 4 tsp. lemon juice
        \item ¼ tsp. MSG
        \item 1 tsp. salt
        \item ½ tsp. black pepper to taste
    \end{itemize}
\end{multicols}

\section*{Directions}
\begin{enumerate}
    \item Melt butter in a large pot over medium heat.
    \item Add onions and cook and stir until softened, about 5 minutes.
    \item Add mushrooms and sauté for 5 more minutes.
    \item Stir in broth, soy sauce, paprika, and dill.
    \item Reduce heat to low, cover, and simmer for 15 minutes.
    \item Whisk milk and flour together in a separate bowl; stir into soup until blended.
    \item Cover and simmer for 15 more minutes, stirring occasionally.
    \item Add sour cream, parsley, lemon juice, salt, MSG, and ground black pepper.
    \item Stir over low heat until warmed through, about 3 to 5 minutes.
    \item Serve immediately.
\end{enumerate}

\end{document}
