\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Rice Crispies Treats}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
	Cooking spray \dotfill \\
	Rice Crispies cereal \dotfill 6 cups \\
	Add-ins (optional) \dotfill ½ cup \\
	Marshmallows \dotfill 16 oz. \\
	Butter, salted \dotfill 8 Tbsp. \\
	Mexican Vanilla \dotfill 1 tsp. \\
	Salt \dotfill pinch \\

\end{multicols}

\section*{Directions}

\begin{enumerate}
	\item Lightly grease 9x9 or 9x13 baking dish and spatula with cooking spray.
	\item In a large bowl, combine dry \textbf{cereal}, 1 cup \textbf{marshmallows}, and other ingredient (such as semi-sweet chocolate chips, M\&M's, or peanut butter chips), set aside.
	\item Melt \textbf{butter} in a large casserole pan (5-6 Qt.) over \textit{medium low} heat.
	\item Add most of the \textbf{marshmallows}.
	\item \textit{Reduce heat to low} and stir until melted.
	\item Add \textbf{vanilla} and a pinch of \textbf{salt}, then mix well.
	\item \textit{Remove from heat}, then add \textbf{cereal}, reserved \textbf{marshmallows}, and optional ingredient
	\item \textit{Mix immediately} using a lightly greased spatula, covering all cereal.
	\item Transfer mixture into baking dish then smooth with a spatula.
\end{enumerate}

Cool for at least one hour before enjoying ---
Cover tightly and store at room temperature up to 4 days ---
Allow to set for one day for best texture and flavor

\end{document}
