\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Dad's Brussels Sprouts •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Brussels sprouts \dotfill 1-2 lb. \\
    Safflower oil \dotfill 2 Tbsp. \\
    Lawry's garlic salt \dotfill 1 tsp. \\
    Butter \dotfill 4 Tbsp. \\
    \columnbreak
    Garlic powder \dotfill \nicefrac{1}{4} tsp. \\
    Dried rosemary \dotfill \nicefrac{1}{4} tsp. \\
    Black pepper \dotfill \nicefrac{1}{4} tsp. \\
    Parmesan cheese, grated \dotfill 2 tsp. \\
    Lemon powder \dotfill \nicefrac{1}{4} tsp. \\
    (or Lemon juice \dotfill 1 Tbsp.)
\end{multicols}

\section*{Directions}

\noindent
Trim and quarter \textbf{Brussels sprouts}

\begin{enumerate}
    \item Clean \textbf{Brussels sprouts} by trimming the stem ends and removing any discolored outer leaves. Cut larger sprouts into quarters and smaller ones in half.
    
    \item In \textit{Large Bowl~\#2}, toss the prepared \textbf{Brussels sprouts} (\textit{Large Bowl~\#1}) with 2~Tbsp. \textbf{oil} and 1~tsp. \textbf{garlic salt} until evenly coated.
    
    \item Spread the \textbf{Brussels sprouts} in the air fryer basket.
    
    \item Air fry at \textit{400°F} for \textit{15~minutes}, shaking the basket halfway through cooking time, until the sprouts are crispy and slightly blackened.
    
    \item While the sprouts are cooking, prepare the butter sauce: In a small saucepan over medium-low heat, melt 4~Tbsp. \textbf{butter}. Add \nicefrac{1}{4}~tsp. \textbf{garlic powder}, \nicefrac{1}{4}~tsp. \textbf{dried rosemary}, and \nicefrac{1}{4}~tsp. \textbf{black pepper}. Cook for \textit{1~minute} until fragrant.
    
    \item Remove butter sauce from heat and whisk in \nicefrac{1}{4}~tsp. \textbf{lemon powder} (or 1~Tbsp. \textbf{lemon juice}).
    
    \item Transfer the cooked \textbf{Brussels sprouts} to a serving bowl, pour the butter sauce over them, and toss to coat evenly.
    
    \item Sprinkle with 2~tsp. grated \textbf{Parmesan cheese} and serve immediately.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Air fryer (3-6 quart capacity)
    \item Large mixing bowl (for tossing sprouts)
    \item Small saucepan (for butter sauce)
    \item Measuring cups and spoons
    \item Sharp knife and cutting board
    \item Wooden spoon or spatula
    \item Whisk
    \item Serving bowl
    \item Timer
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Trim and quarter \textbf{Brussels sprouts} before preheating the air fryer
    \item Measure all spices and have them ready by the stovetop
    \item Have butter at room temperature for faster melting
    \item If using \textbf{lemon juice}, squeeze fresh just before adding to the sauce
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Choose firm, bright green \textbf{Brussels sprouts} with tightly packed leaves
    \item Smaller sprouts tend to be sweeter and cook more evenly
    \item Use a high smoke-point neutral oil like avocado, canola, or grapeseed
    \item European-style butter (higher fat content) creates a richer sauce
    \item Freshly grated \textbf{Parmesan} provides better flavor than pre-grated
    \item Fresh rosemary (1 tsp. finely chopped) can be substituted for dried
    \item If you don't have \textbf{TruLemon}, fresh lemon zest can be used in addition to juice
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Size consistency matters - cut larger sprouts into quarters and smaller ones in half for even cooking
    \item Don't overcrowd the air fryer basket - cook in batches if needed for maximum crispiness
    \item For extra caramelization, place sprouts cut-side down in the basket
    \item If sprouts aren't crispy enough after the initial cooking time, air fry for an additional \textit{2-3~minutes}
    \item Keep the butter sauce warm until ready to toss with the sprouts
    \item Add the \textbf{Parmesan} just before serving for the best texture
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item \textbf{Brussels sprouts} can be trimmed and quartered up to \textit{24~hours} in advance and stored in an airtight container in the refrigerator
    \item Butter sauce can be prepared \textit{1~hour} ahead and kept warm on the lowest heat setting
    \item Leftover sprouts can be refrigerated for up to \textit{3~days} and reheated in the air fryer at \textit{350°F} for \textit{3-4~minutes}
    \item Not recommended for freezing as texture will deteriorate
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve as a side dish with roasted chicken, steak, or pork chops
    \item Add crispy bacon bits or toasted pine nuts as a deluxe garnish
    \item For a vegetarian main course, serve over creamy polenta or risotto
    \item Pairs well with rich, full-bodied red wines like Cabernet Sauvignon
    \item For a holiday meal, add dried cranberries for a pop of color and sweetness
\end{itemize}

\end{multicols}
}

\end{document}