\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Fried Rice  •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Canola oil \dotfill 3 Tbsp. \\
    Sesame oil \dotfill 2 Tbsp. \\
    Cooked parboiled rice,  cold \dotfill 6 cups \\
    Onion, finely diced \dotfill \nicefrac{1}{3} cup \\
    Carrot, finely grated \dotfill \nicefrac{1}{3} cup \\
    Garlic, minced \dotfill 3 cloves \\
    Ginger, finely grated \dotfill 1 tsp. \\
    Eggs \dotfill 2 \\
    \columnbreak
    Frozen peas \dotfill \nicefrac{3}{4} cup \\
    Soy sauce \dotfill 3 Tbsp. \\
    Fish sauce \dotfill 2 tsp. \\
    Hoisin sauce (optional) \dotfill 1 tsp. \\
    Sesame seeds \dotfill 1 Tbsp. \\
    Scallions, diced \dotfill \nicefrac{1}{3} cup \\
\end{multicols}

\section*{Directions}

\noindent
\textit{1-2~days ahead}: Prepare Uncle Ben's parboiled rice, rinse and cook according to rice maker instructions ---
Finely dice \textbf{onion}; set aside in \textit{Small Bowl~\#1} ---
Grate \textbf{carrot} and \textbf{ginger}; combine in \textit{Small Bowl~\#2} ---
Mince \textbf{garlic}; set aside in \textit{Small Bowl~\#3} ---
Dice \textbf{scallions}; set aside in \textit{Small Bowl~\#4} ---
Scramble \textbf{eggs}; set aside in \textit{Small Bowl~\#5}

\begin{enumerate}
	\item In \textit{Small Bowl~\#6}, combine 3~Tbsp. \textbf{soy sauce}, 2~tsp. \textbf{fish sauce}, 1~tsp. \textbf{hoisin sauce} (optional), and 1~Tbsp. \textbf{sesame seeds}
    \item Heat large high-walled frying pan or wok on \textit{High}.
    \item Add 3~Tbsp. \textbf{canola oil} and heat for \textit{30~seconds}.
    \item Add 6~cups \textbf{rice} to pan and stir thoroughly. Pan should be hot enough that rice makes popping sounds.
    \item Stir \textbf{rice} every \textit{30~seconds} for about \textit{5~minutes} until moisture is reduced and rice begins to change color.
    \item Create an empty circle in center of pan and add \textbf{onion} (\nicefrac{1}{3}~cup, \textit{Small Bowl~\#1}), \textbf{carrot} and \textbf{ginger} (\textit{Small Bowl~\#2}), and \textbf{garlic} (\textit{Small Bowl~\#3}).
    \item Add 1~Tbsp. \textbf{sesame oil} to vegetables in pan.
    \item Cook and stir vegetables carefully for \textit{1~minute}, avoiding combining with rice.
    \item Stir contents of pan thoroughly.
    \item Create an empty circle in center of pan and add scrambled \textbf{eggs} (\textit{Small Bowl~\#5}).
    \item Add remaining 1~Tbsp. \textbf{sesame oil} to eggs.
    \item Cook, stir, and chop eggs carefully for about \textit{1~minute} until set, avoiding combining with rice.
    \item Stir contents of pan thoroughly.
    \item Add \nicefrac{3}{4}~cup \textbf{peas} and stir thoroughly.
    \item Add prepared sauce mixture (\textit{Small Bowl~\#6}) and stir thoroughly.
    \item Cook for about \textit{1~minute}, stirring frequently.
    \item Add \textbf{scallions} (\nicefrac{1}{3}~cup, \textit{Small Bowl~\#4}) and stir thoroughly.
    \item Remove from heat and serve hot.
\end{enumerate}

\end{document}
