\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Leta's Fruit Crunch}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Frozen mixed berries \dotfill 4 cups \\
    Brown sugar \dotfill ¼ cup \\
    All-purpose flour (130g)\dotfill 1 cup \\
    Sugar \dotfill 1 cup \\
    Salt \dotfill 1 tsp. \\
    Cinnamon \dotfill 1 tsp. \\
    Eggs \dotfill 2 large \\
    Butter \dotfill 4 Tbsp.
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{375°F} ---
Lightly beat \textbf{eggs} ---
Melt \textbf{butter} ---
Grease 8x8 inch glass baking dish

\begin{enumerate}
    \item Mix \textbf{frozen berries} with \textbf{brown sugar} and spread in a baking dish.
    
    \item In a bowl, combine \textbf{flour}, \textbf{sugar}, \textbf{salt}, and \textbf{cinnamon}.
    
    \item Using a whisk, gradually add beaten \textbf{egg} to the flour mixture, a small amount at a time with a spoon.
    
    \textit{\textbf{IMPORTANT:} Use a chopping motion with the whisk (not stirring) to incorporate each addition of egg until the mixture reaches a clumpy wet sand consistency. Be patient and methodical, and do not use all of the egg.}
    
    \item Sprinkle the crumble mixture evenly over the \textbf{fruit}.
    
    \item Pour melted \textbf{butter} over the top.
    
    \item Bake for \textit{60-75~minutes} until golden brown and bubbly.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 8x8 inch glass baking dish
    \item Large mixing bowl
    \item Small bowl for beaten egg
    \item Whisk
    \item Measuring cups and spoons
    \item Small saucepan or microwave-safe bowl for melting butter
    \item Rubber spatula
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Keep \textbf{fruit} frozen until ready to use
    \item Beat \textbf{eggs} before starting
    \item Measure all ingredients before beginning
    \item Have whisk ready for proper mixing technique
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use frozen mixed berries straight from freezer
    \item If \textbf{fruit} has excess ice crystals, do not thaw, simply break up any large clumps
    \item Large \textbf{eggs} should be at room temperature for better incorporation
    \item Standard salted or unsalted butter works well
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item The chopping motion with the whisk is crucial - do not stir
    \item Add \textbf{egg} very gradually, small amounts at a time
    \item The mixture should resemble wet sand before topping the fruit
    \item Spread topping evenly but do not pack it down
    \item Pour \textbf{butter} evenly over the entire surface
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Best served warm from the oven
    \item Can be assembled and refrigerated for up to \textit{24~hours} before baking
    \item Leftovers keep well covered at room temperature for \textit{2~days} or refrigerated for \textit{7 days}
    \item Reheat individual portions in microwave for \textit{30~seconds}
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve warm with vanilla ice cream
    \item Allow to cool for \textit{10~minutes} before serving
\end{itemize}

\end{multicols}
}

\end{document}