\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Peanut Butter Cookies}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{quote}
\small
\begin{em}
Classic peanut butter cookies with a perfectly crisp exterior and soft center, finished with the traditional crisscross pattern. \\
\\
Makes 2 dozen.
\end{em}
\end{quote}

\section*{Ingredients}
\begin{multicols}{2}
\noindent
    Peanut butter (JIF creamy) \dotfill 1¼ cups \\
    Eggs, large \dotfill 2 \\
    Sugar \dotfill 1 cup \\
    Baking soda \dotfill 1 tsp. \\
    Mexican vanilla \dotfill 1 tsp. \\
    Coarse salt \dotfill ½ tsp. \\
    Additional sugar for sprinkling
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{350°F} -- 

\begin{enumerate}
    \item In a large bowl, combine \textbf{peanut~butter}, \textbf{eggs}, \textbf{sugar}, \textbf{baking~soda}, \\\textbf{Mexican~vanilla}, and \textbf{salt} until well mixed.
    \item Using a 1¾" cookie scoop, drop dough onto ungreased cookie sheets, spacing balls 2 inches apart.
    \item Press each cookie with a fork twice, creating a crisscross pattern on top.
    \item Sprinkle cookies with additional \textbf{sugar}.
    \item Bake for \textit{12-13~minutes} until edges are set. If baking two sheets at once, rotate their positions after \textit{6~minutes}.
    \item Let cookies cool on cookie sheet for \textit{3-5~minutes} before transferring to a wire rack.
\end{enumerate}

\end{document}
