\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Spam Musubi •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Spam, low salt \dotfill 1 (12 oz.) can \\
    Soy sauce, low salt \dotfill ¼ cup \\
    Mirin \dotfill 1/3 cup \\
    Brown sugar \dotfill 2 Tbsp. \\
    Sake \dotfill 2 Tbsp. \\
    Sushi rice, cooked \dotfill 3 cups \\
    Nori sheets \dotfill 4 \\
    Kewpie mayonnaise \dotfill ½ cup \\
    Sriracha sauce \dotfill 1½ Tbsp. \\
    Toasted sesame oil \dotfill 1 tsp. \\
    Neutral oil \dotfill 2 Tbsp. \\
    Toasted sesame seeds \dotfill 1 Tbsp.
\end{multicols}

\section*{Directions}

\noindent
\textit{Using a musubi mold and spam slicer will be helpful} ---
Cook \textbf{rice} ---
Slice \textbf{Spam} into 10-12 even pieces ---
Cut \textbf{nori sheets} into thirds

\begin{enumerate}
    \item For the sriracha mayo:
    \begin{enumerate}
        \item Combine and mix \textbf{Kewpie~mayonnaise}, \textbf{Sriracha}, and \textbf{sesame~oil}, in a small bowl
        \item Refrigerate until needed
    \end{enumerate}
    
    \item Heat \textbf{oil} in a pan over medium heat. Working in batches if needed, fry \textbf{Spam} slices for \textit{2-3~minutes} per side until browned and crispy.
    
    \item In a small bowl, whisk together \textbf{soy~sauce}, \textbf{mirin}, \textbf{brown~sugar}, and \textbf{sake}. 
    
    \item Add sauce mixture to pan with \textbf{Spam} and swirl to coat evenly. Simmer for \textit{5~minutes} until liquid is nearly absorbed.
    
    \item Using a musubi mold, layer ingredients as follows:
    \begin{itemize}
        \item Place a strip of \textbf{nori} on work surface
        \item Press \textbf{rice} (\textit{¼~cup}) into mold on center of \textbf{nori}
        \item Add 1 piece of glazed \textbf{Spam}
        \item Top with \textit{1~teaspoon} sriracha mayo and prinkle with furikake (or toasted sesame seeds)
    \end{itemize}
    
    \item Slide mold off musubi and fold \textbf{nori} ends up and over to seal, using a drop of water to secure.
    
    \item Serve immediately or wrap individually in plastic wrap. Store in refrigerator for up to \textit{5~days}.
\end{enumerate}

\end{document}