\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Spinach and Artichoke Dip}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Artichoke hearts \dotfill 2 (14 oz.) cans \\
    Spinach (fresh) \dotfill 10 oz. \\
    Cream cheese, softened \dotfill 8 oz. \\
    Mayonnaise \dotfill ½ cup \\
    Sour cream \dotfill ½ cup \\
    Garlic cloves \dotfill 3 \\
    Parmesan, grated \dotfill 4 oz. \\
    Mozzarella, shredded \dotfill 8 oz. \\
    Salt \dotfill ½ tsp. \\
    Black pepper \dotfill ½ tsp. \\
    Red pepper flakes \dotfill ½ tsp. \\
    MSG \dotfill ¼ tsp. \\
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{375°F} ---
Drain and chop \textbf{artichoke hearts} ---
Rough chop \textbf{fresh spinach} ---
Mince \textbf{garlic}

\begin{enumerate}
    \item In a large bowl, combine softened \textbf{cream cheese}, \textbf{mayonnaise}, and \textbf{sour cream} until smooth.
    
    \item Mix in minced \textbf{garlic}, \textbf{salt}, \textbf{black pepper}, \textbf{red pepper flakes}, and \textbf{MSG}.
    
    \item Fold in chopped \textbf{artichoke hearts}, chopped \textbf{spinach}, \textbf{Parmesan}, and half of \textbf{mozzarella}.
    
    \item Transfer mixture to a 2-quart baking dish and top with remaining \textbf{mozzarella}.
    
    \item Bake for \textit{30-35 minutes} until bubbly and golden brown on top.
    
    \item Let rest for \textit{5-10 minutes} before serving.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 2-quart baking dish (ceramic or glass)
    \item Large mixing bowl (for combining ingredients)
    \item Medium bowl (for cheese)
    \item Cutting board and sharp knife
    \item Measuring cups and spoons
    \item Rubber spatula or wooden spoon
    \item Garlic press (optional)
    \item Colander (for draining artichokes)
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Remove \textbf{cream cheese} from refrigerator at least \textit{1~hour} before starting
    \item Drain \textbf{artichoke hearts} thoroughly before chopping
    \item Grate cheeses while \textbf{cream cheese} is softening
    \item Have all ingredients measured and ready before assembly
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use artichoke hearts packed in water rather than marinated varieties
    \item Fresh spinach provides better texture than frozen, but if using frozen, thaw and squeeze out all excess moisture
    \item Full-fat dairy products yield the best texture and flavor
    \item For extra flavor, add a pinch of cayenne or increase \textbf{red pepper flakes}
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Rough chop spinach and artichokes for better texture - avoid fine chopping
    \item Don't overmix after adding \textbf{spinach} and \textbf{artichokes} to maintain texture
    \item Press \textbf{garlic} just before mixing to maximize flavor
    \item For best browning, add final layer of \textbf{mozzarella} just before baking
    \item If top browns too quickly, cover loosely with foil
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Can be assembled up to \textit{24~hours} in advance and refrigerated
    \item If made ahead, bring to room temperature for \textit{30~minutes} before baking
    \item Leftovers can be refrigerated for up to \textit{3~days}
    \item Reheat in \textit{350°F} oven until warm, about \textit{15-20~minutes}
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve with toasted baguette slices, crackers, or fresh vegetables
    \item For best texture, allow to cool slightly before serving
    \item Garnish with fresh cracked pepper or chopped parsley if desired
    \item Pairs well with a crisp white wine or light beer
\end{itemize}

\end{multicols}
}

\end{document}