\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Mexican Street Corn (Elote-Style) •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Sweet corn \dotfill 2 (15 oz.) cans \\
    Vegetable oil \dotfill 2 Tbsp. \\
    Mexican spice mix \dotfill 1 Tbsp. \\
    Mayonnaise \dotfill 2 Tbsp. \\
    \columnbreak
    Fresh lime \dotfill ½ \\
    Fresh cilantro, chopped \dotfill ¼ cup \\
    Queso fresco, crumbled \dotfill 3 Tbsp. \\
\end{multicols}

\section*{Directions}

\noindent
Drain \textbf{corn} ---
Chop \textbf{cilantro} ---
Crumble \textbf{queso~fresco} ---
Juice \textbf{lime}

\begin{enumerate}
    \item Heat \textbf{vegetable~oil} in a large skillet over medium-high heat until shimmering.
    
    \item Add drained \textbf{corn} in a single layer. Cook undisturbed for \textit{3-4~minutes} until kernels develop golden-brown caramelization.
    
    \item Stir \textbf{corn} and continue cooking \textit{2-3~minutes}, allowing additional browning and caramelization.
    
    \item Sprinkle \textbf{Mexican~spice~mix} over \textbf{corn} and stir constantly for \textit{30~seconds} until fragrant and evenly distributed.
    
    \item Remove skillet from heat. Squeeze \textbf{lime~juice} over \textbf{corn}, then add \textbf{mayonnaise}, stirring until kernels are evenly coated.
    
    \item Fold in chopped \textbf{cilantro} and crumbled \textbf{queso~fresco}, gently mixing until \textbf{cilantro} wilts and \textbf{cheese} begins to soften and melt into the mixture.
    
    \item Transfer to serving bowl and serve immediately while warm.
\end{enumerate}

\textit{Serves 4-6 as a side dish}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Large skillet or sauté pan (12-inch recommended)
    \item Serving bowl (medium size)
    \item Measuring spoons and cups
    \item Sharp knife for chopping cilantro
    \item Cutting board
    \item Can opener
    \item Colander for draining corn
    \item Wooden spoon or spatula for stirring
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Drain \textbf{corn} thoroughly in colander
    \item Chop \textbf{cilantro} into small pieces
    \item Crumble \textbf{queso~fresco} by hand or with fork
    \item Cut \textbf{lime} in half and juice one half
    \item Measure all ingredients before heating pan
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Fire-roasted \textbf{corn} varieties add extra smoky depth
    \item \textbf{Mexican~spice~mix} should contain chili powder, cumin, and paprika at minimum
    \item Fresh \textbf{lime} juice is essential - bottled juice lacks brightness
    \item \textbf{Queso~fresco} can be substituted with cotija or mild feta
    \item Full-fat \textbf{mayonnaise} provides best texture and richness
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Don't move \textbf{corn} too early - caramelization requires direct contact
    \item \textbf{Spice~mix} should sizzle when added - this blooms the aromatics
    \item Remove from heat before adding \textbf{lime} and \textbf{mayo} to prevent breaking
    \item Fold \textbf{cilantro} and \textbf{cheese} gently to maintain texture
    \item Serve immediately for best flavor and temperature contrast
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Best served fresh and hot from the pan
    \item Can be reheated gently in skillet over low heat
    \item Leftovers keep \textit{2~days} refrigerated
    \item Add fresh \textbf{cilantro} and \textbf{lime} when reheating
    \item May need additional \textbf{mayonnaise} if mixture seems dry
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Excellent alongside grilled meats or fish
    \item Perfect for taco nights and Mexican-themed meals
    \item Serve with additional \textbf{lime} wedges and hot sauce
    \item Can be served as appetizer with tortilla chips
    \item Pairs well with cold Mexican beer or agua fresca
    \item Garnish with extra \textbf{queso~fresco} if desired
\end{itemize}

\end{multicols}
}

\end{document}