\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Gluten-Free Holiday Stuffing}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    G.F. bread, cubed \dotfill 1 loaf (8-10 cups) \\
    Sage breakfast sausage \dotfill 1 lb. \\
    Butter \dotfill 8 Tbsp. \\
    Onions, medium \dotfill 2 \\
    Celery stalks \dotfill 4 \\
    Garlic cloves \dotfill 3 \\
    \columnbreak
    Dried sage \dotfill 2 tsp. \\
    Dried rosemary \dotfill 1 tsp. \\
    Dried thyme \dotfill 2 tsp. \\
    Dried parsley \dotfill 1 Tbsp. \\
    Ground nutmeg \dotfill 1/8 tsp. \\
    Chicken broth \dotfill 2-3 cups \\
    Eggs \dotfill 2 large \\
    Kosher salt \dotfill 1½ tsp. \\
    Black pepper \dotfill 1 tsp.
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{250°F} for bread, then \textit{350°F} for baking ---
Cut \textbf{bread} into 1-inch cubes ---
Dice \textbf{onions} and \textbf{celery} ---
Mince \textbf{garlic} ---
Beat \textbf{eggs} ---
Grease a 9x13 inch baking dish ---
Melt 3 \textbf{Tbsp. butter} for bread cubes, remaining for vegetables

\begin{enumerate}
    \item Toss \textbf{bread cubes} with 4 Tbsp. melted \textbf{butter}, then spread on a baking sheet and toast at \textit{250°F} for \textit{45-60~minutes}, stirring every \textit{15~minutes}, until golden and dry. Let cool.
    
    \item Brown \textbf{sage breakfast sausage} over medium heat until cooked through, breaking into small crumbles. Remove with slotted spoon and set aside.
    
    \item In the same pan, melt remaining 4 \textbf{Tbsp. butter}. Add \textbf{onions} and \textbf{celery}, cooking until softened, about \textit{8-10~minutes}. Add \textbf{garlic} and cook for \textit{1~minute} more.
    
    \item In a large bowl, combine toasted \textbf{bread cubes}, cooked \textbf{sausage}, sautéed vegetables, \textbf{dried sage}, \textbf{dried rosemary}, \textbf{dried thyme}, \textbf{dried parsley}, and \textbf{ground nutmeg}.
    
    \item Gradually add \textbf{chicken broth}, stirring gently until bread is evenly moist but not soggy. Mix in beaten \textbf{eggs}, 1½ tsp. \textbf{kosher salt}, and 1 tsp. \textbf{black pepper}. Taste and adjust seasoning if needed - the mixture should taste slightly saltier than you'd expect, as the flavors will mellow during baking.
    
    \item Transfer to prepared baking dish. Cover with foil and bake at \textit{350°F} for \textit{30~minutes}.
    
    \item Uncover and bake for additional \textit{15-20~minutes} until top is golden brown and crispy.
    
    \item Let rest for \textit{10~minutes} before serving.
\end{enumerate}

\end{document}