\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Green Bean Casserole}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Green beans, fresh \dotfill 1½ lbs \\
    Butter \dotfill ½ cup \\
    Mushrooms, fresh \dotfill ½ lb \\
    Onion, small \dotfill 1 \\
    All-purpose flour \dotfill ¼ cup \\
    Whole milk \dotfill 1½ cups \\
    \columnbreak
    Sour cream \dotfill 1 cup \\
    Cheddar cheese, shredded \dotfill 1 cup \\
    Salt \dotfill 1 tsp \\
    Black pepper \dotfill 1 tsp \\
    French-fried onions \dotfill 2 cups
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{350°F} ---
Trim \textbf{green~beans} ---
Slice \textbf{mushrooms} ---
Chop \textbf{onion} ---
Shred \textbf{cheddar~cheese} ---
Grease a 2½-quart baking dish

\begin{enumerate}
    \item Bring a large pot of water to a boil. Add \textbf{green~beans} and blanch for \textit{5~minutes}. Drain and immediately plunge into ice water. Drain again.
    
    \item In a large skillet, melt \textbf{butter} over medium heat. Add \textbf{mushrooms} and \textbf{onion}; cook for \textit{5~minutes}, until tender.
    
    \item Stir in \textbf{flour} and cook for \textit{2~minutes}, stirring constantly.
    
    \item Gradually stir in \textbf{milk} and cook for \textit{2-3~minutes}, until mixture thickens.
    
    \item Stir in \textbf{sour~cream}, \textbf{cheese}, \textbf{salt}, \textbf{pepper}, and blanched \textbf{green~beans}.
    
    \item Transfer mixture to prepared baking dish. Bake for \textit{25~minutes}.
    
    \item Sprinkle evenly with \textbf{French-fried~onions}. Bake for \textit{15~minutes} longer, until hot and bubbly.
\end{enumerate}

\end{document}
