\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Holiday Stuffing  •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Bread, cubed \dotfill 1 lb. (8-10 cups) \\
    Sage breakfast sausage \dotfill 1 lb. \\
    Butter \dotfill 8 Tbsp. \\
    Onions, medium \dotfill 2 \\
    Celery stalks \dotfill 4 \\
    Garlic cloves \dotfill 3 \\
    \columnbreak
    Dried sage \dotfill 2 tsp. \\
    Dried rosemary \dotfill 1 tsp. \\
    Dried thyme \dotfill 2 tsp. \\
    Dried parsley \dotfill 1 Tbsp. \\
    Ground nutmeg \dotfill \nicefrac{1}{8} tsp. \\
    Chicken broth \dotfill 2-3 cups \\
    Eggs \dotfill 2 large \\
    Kosher salt \dotfill 1\nicefrac{1}{2} tsp. \\
    Black pepper \dotfill 1 tsp.
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{250°F} for bread, then \textit{350°F} for baking ---
Cut \textbf{bread} into \nicefrac{1}{2}~inch cubes; set aside in \textit{Large Bowl~\#1} ---
Dice \textbf{onions} and \textbf{celery}; combine in \textit{Medium Bowl~\#1} ---
Mince \textbf{garlic}; set aside in \textit{Small Bowl~\#1} ---
Beat \textbf{eggs}; set aside in \textit{Small Bowl~\#2} ---
Grease a 9~inch×13~inch baking dish ---
Melt 4~Tbsp. \textbf{butter} for bread cubes in \textit{Small Bowl~\#3}, remaining 4~Tbsp. for vegetables in \textit{Small Bowl~\#4}

\begin{enumerate}
    \item Toss \textbf{bread cubes} (\textit{Large Bowl~\#1}) with melted \textbf{butter} (4~Tbsp., \textit{Small Bowl~\#3}), then spread on a baking sheet and toast at \textit{250°F} for \textit{45-60~minutes}, stirring every \textit{15~minutes}, until golden and dry. Let cool and return to \textit{Large Bowl~\#1}.
    
    \item Brown \textbf{sausage} over medium heat until cooked through, breaking into small crumbles. Remove with slotted spoon and transfer to \textit{Medium Bowl~\#2}; set aside.
    
    \item In the same pan, melt remaining 4~Tbsp. \textbf{butter} (\textit{Small Bowl~\#4}). Add \textbf{onions} and \textbf{celery} (\textit{Medium Bowl~\#1}), cooking until softened, about \textit{8-10~minutes}. Add \textbf{garlic} (\textit{Small Bowl~\#1}) and cook for \textit{1~minute} more. Transfer to \textit{Medium Bowl~\#3}; set aside.
    
    \item In \textit{Large Bowl~\#2}, combine toasted \textbf{bread} (\textit{Large Bowl~\#1}), cooked \textbf{sausage} (\textit{Medium Bowl~\#2}), sautéed vegetables (\textit{Medium Bowl~\#3}), 2~tsp. \textbf{dried sage}, 1~tsp. \textbf{dried rosemary}, 2~tsp. \textbf{dried thyme}, 1~Tbsp. \textbf{dried parsley}, and \nicefrac{1}{8}~tsp. \textbf{ground nutmeg}.
    
    \item Gradually add \textbf{chicken broth} (2-3~cups), stirring gently until bread is evenly moist but not soggy. Mix in beaten \textbf{eggs} (\textit{Small Bowl~\#2}), 1\nicefrac{1}{2}~tsp. \textbf{kosher salt}, and 1~tsp. \textbf{black pepper}. Taste and adjust seasoning if needed - the mixture should taste slightly saltier than you'd expect, as the flavors will mellow during baking.
    
    \item Transfer to prepared baking dish. Cover with foil and bake at \textit{350°F} for \textit{30~minutes}.
    
    \item Uncover and bake for additional \textit{15-20~minutes} until top is golden brown and crispy.
    
    \item Let rest for \textit{10~minutes} before serving.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 9x13 inch baking dish
    \item Large rimmed baking sheet for toasting bread
    \item Large skillet or sauté pan
    \item Large mixing bowl (at least 6-quart capacity)
    \item Medium bowl for beaten eggs
    \item Measuring cups and spoons
    \item Sharp knife and cutting board
    \item Wooden spoon or spatula
    \item Aluminum foil
    \item Slotted spoon
    \item Timer
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Measure and prepare all ingredients before starting
    \item Bring refrigerated ingredients to room temperature
    \item Dice vegetables and measure herbs
\end{itemize}

\subsection*{Ingredient and Preparation Tips}
\begin{itemize}
    \item Choose hearty bread varieties for best texture
    \item Use high-quality bulk \textbf{sage sausage}, or Jimmy Dean
    \item Fresh herbs can be substituted at triple the quantity
    \item Cut bread into uniform ½-inch cubes for even toasting
    \item Add \textbf{broth} gradually - absorption varies by bread type
    \item Test seasoning before adding \textbf{eggs}, then fold gently to maintain texture
    \item European-style butter provides richer flavor
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Toast bread up to \textit{3~days} ahead; store in airtight container
    \item Assemble up to \textit{24~hours} before baking
    \item Bring refrigerated stuffing to room temperature for \textit{30~minutes}
    \item Add extra \textbf{broth} if needed after refrigeration
    \item Leftovers keep \textit{3~days}; reheat covered at \textit{350°F} for \textit{20~minutes}
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve alongside turkey or chicken
    \item Can be baked inside poultry or separately
    \item Garnish with fresh sage and extra gravy
    \item Transform leftovers into breakfast waffles
    \item Optional: top with toasted gluten-free breadcrumbs for extra crunch
\end{itemize}

\end{multicols}
}

\end{document}