\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Jamaican Jerk Seasoning}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}


\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Ground allspice \dotfill 3 Tbsp. \\
    Dark brown sugar \dotfill 2 Tbsp. \\
    Scotch bonnet powder \dotfill 1\nicefrac{1}{2} Tbsp. \\
    Onion powder \dotfill 2 Tbsp. \\
    Garlic powder \dotfill 2 Tbsp. \\
    Thyme, dried \dotfill 2 Tbsp. \\
    Ginger, ground \dotfill 1 Tbsp. \\
	\columnbreak
    Green onion, dried \dotfill 1 Tbsp. \\
    Black pepper, ground \dotfill 2 tsp. \\
    Cinnamon, ground \dotfill 1 tsp. \\
    Nutmeg, ground \dotfill 1 tsp. \\
    Cloves, ground \dotfill \nicefrac{1}{2} tsp. \\
    Coriander, ground \dotfill 1 tsp. \\
    TruLime powder \dotfill 2 tsp. \\
    Kosher salt \dotfill 1 Tbsp. \\
\end{multicols}

\section*{Directions}

\noindent
Gather all spices and powders ---
Have measuring spoons ready ---
Prepare airtight container for storage

\begin{enumerate}
    \item Measure all ingredients accurately and add to a large mixing bowl: \textbf{ground allspice}, \textbf{brown sugar}, \textbf{scotch bonnet powder}, \textbf{onion powder}, \textbf{garlic powder}, \textbf{dried thyme}, \textbf{ground ginger}, \textbf{dried green onion}, \textbf{ground black pepper}, \textbf{ground cinnamon}, \textbf{ground nutmeg}, \textbf{ground cloves}, \textbf{ground coriander}, \textbf{TruLime powder}, and \textbf{kosher salt}.
    
    \item Whisk thoroughly until all ingredients are well incorporated and the mixture appears uniform in color with no visible clumps.
    
    \item Transfer to an airtight container or glass jar with a tight-fitting lid.
    
    \item Allow flavors to marry for at least \textit{24~hours} before using for best results.
    
    \item Store in a cool, dark place for up to \textit{6~months}.
\end{enumerate}

\end{document}