\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.2in,right=1.2in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Peanut Butter Cookies •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Peanut butter (creamy) \dotfill 1\nicefrac{1}{4} cups \\
    Eggs, large \dotfill 2 \\
    Sugar \dotfill 1 cup \\
    Granulated sugar (for rolling) \dotfill \nicefrac{1}{4} cup \\
    Baking soda \dotfill 1 tsp. \\
    Mexican vanilla \dotfill 1 tsp. \\
    Salt \dotfill 1 tsp.
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{350°F} ---
Bring \textbf{peanut butter} and \textbf{eggs} to room temperature ---
Line baking sheets with parchment paper ---
Place \textbf{rolling sugar} in shallow dish

\begin{enumerate}
    \item Mix the dough in a large bowl:
    \begin{enumerate}
        \item Stir room temperature \textbf{peanut~butter} and \textbf{sugar} vigorously with a sturdy spatula or wooden spoon until smooth and no visible sugar granules remain, about \textit{3--5~minutes}. Scrape bowl as needed. (Or use a hand mixer or stand mixer on medium for about \textit{1--2~minutes}.)
        \item Add \textbf{eggs} one at a time, mixing well after each until fully incorporated.
        \item Add \textbf{Mexican~vanilla} and mix until combined.
        \item Add \textbf{baking~soda} and \textbf{salt} and stir until just combined; dough should be smooth and uniform.
    \end{enumerate}
    \item Cover bowl and chill dough for \textit{15~minutes} to make it easier to handle.
    
    \item Using a 1\nicefrac{3}{4}~inch cookie scoop or rounded tablespoon, portion dough into balls.
    
    \item Roll each ball in \textbf{granulated~sugar} until completely coated.
    
    \item Place sugared balls on prepared baking sheets, spacing 2 inches apart.
    
    \item Press each cookie with a fork twice, creating a crisscross pattern on top. If fork sticks to dough, dip it in the \textbf{rolling~sugar} between cookies.
    
    \item Bake for \textit{12-13~minutes} until edges are lightly golden but centers still appear soft. If baking two sheets at once, rotate their positions halfway through baking.
    
    \item Let cookies cool on baking sheet for \textit{5~minutes} before transferring to a wire rack to cool completely.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Large mixing bowl
    \item Sturdy spatula or wooden spoon
    \item 1\nicefrac{3}{4}~inch cookie scoop or tablespoon measure
    \item Baking sheets
    \item Parchment paper
    \item Measuring cups and spoons
    \item Fork for creating pattern
    \item Shallow dish for rolling sugar
    \item Wire cooling rack
    \item Rubber spatula
    \item Hand mixer or stand mixer (optional)
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Remove \textbf{peanut~butter} and \textbf{eggs} from refrigerator \textit{1~hour} before starting
    \item Line baking sheets with parchment
    \item Measure all ingredients before beginning
    \item Set up sugar rolling station
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use commercial creamy peanut butter (like JIF or Skippy) rather than natural style
    \item Room temperature \textbf{peanut~butter} creates a smoother dough
    \item For extra crunch, use coarse sugar for rolling
    \item Mexican vanilla adds depth, but pure vanilla extract can substitute
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Don't skip the \textit{15~minute} chill time - it makes the dough easier to handle
    \item Keep cookie size consistent for even baking
    \item Press fork just deep enough to create pattern without flattening cookies too much
    \item Cookies will appear slightly underbaked when done but will set as they cool
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Dough can be chilled up to \textit{24~hours}
    \item Baked cookies keep in airtight container for \textit{5~days}
    \item Freeze baked cookies up to \textit{3~months}
    \item Freeze portioned dough balls up to \textit{3~months} - roll in sugar after thawing
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Best served at room temperature
    \item Excellent with cold milk or hot coffee
    \item Crumble over vanilla ice cream
    \item Pack in lunch boxes or cookie tins
    \item Use as base for ice cream sandwiches
\end{itemize}

\end{multicols}
}

\end{document}