\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.1,AutoFakeBold=1.3,AutoFakeSlant=0.3]{Doves Type}

\title{Italian Sausage \& San Marzano Tomato Sauce •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Italian sausage \dotfill 1 lb. \\
    Yellow onion, large \dotfill 1 \\
    Carrots, medium \dotfill 2 \\
    Garlic cloves \dotfill 8 \\
    Zucchini, medium \dotfill 1 \\
    Mushrooms, sliced \dotfill 8 oz. can \\
    Red wine \dotfill 8 oz. \\
    \columnbreak
    Prego chunky garden style sauce \dotfill 24 oz. jar \\
    San Marzano tomatoes, whole \dotfill 24 oz. can \\
    Tomato paste \dotfill 3 Tbsp. \\
    Italian seasoning \dotfill 2-3 Tbsp. \\
    Brown sugar \dotfill \nicefrac{1}{4} cup \\
    Chicken stock \dotfill as needed \\
    Lemon juice \dotfill 3 Tbsp. \\
\end{multicols}

\section*{Directions}

\noindent
Dice \textbf{onion}; set aside in \textit{Medium Bowl~\#1} ---
Dice \textbf{carrots} fine; set aside in \textit{Medium Bowl~\#2} ---
Mince \textbf{garlic}; set aside in \textit{Small Bowl~\#1} ---
Quarter \textbf{zucchini} lengthwise and slice into \nicefrac{1}{4}~inch pieces; set aside in \textit{Medium Bowl~\#3} ---
Drain \textbf{mushrooms}; set aside in \textit{Medium Bowl~\#4} ---
Crush \textbf{San Marzano tomatoes} by hand; set aside in \textit{Large Bowl~\#1} ---
Open \textbf{red wine} to breathe

\begin{enumerate}
    \item In a large, heavy-bottomed pot or Dutch oven, brown \textbf{Italian~sausage} over medium-high heat, breaking into bite-sized pieces. Cook until well-browned and cooked through, about \textit{8-10~minutes}. Remove \textbf{sausage} with slotted spoon and set aside, leaving rendered fat in pot.
    
    \item Reduce heat to medium and add diced \textbf{onion} (\textit{Medium Bowl~\#1}) to the rendered fat. Cook until translucent and softened, about \textit{5~minutes}.
    
    \item Add diced \textbf{carrots} (\textit{Medium Bowl~\#2}) and cook for additional \textit{5~minutes}, stirring occasionally.
    
    \item Add minced \textbf{garlic} (\textit{Small Bowl~\#1}), sliced \textbf{zucchini} (\textit{Medium Bowl~\#3}), and drained \textbf{mushrooms} (\textit{Medium Bowl~\#4}). Cook for \textit{2-3~minutes} until \textbf{garlic} is fragrant.
    
    \item Pour in 8~oz. \textbf{red wine} to deglaze, scraping up any browned bits from bottom of pot. Cook until wine reduces by half, about \textit{3-4~minutes}.
    
    \item Stir in 3~Tbsp. \textbf{tomato paste} and cook for \textit{1-2~minutes} until it darkens slightly and becomes fragrant.
    
    \item Add 24~oz. \textbf{Prego sauce}, hand-crushed \textbf{San Marzano tomatoes} with their juices (\textit{Large Bowl~\#1}), 2-3~Tbsp. \textbf{Italian seasoning}, and \nicefrac{1}{4}~cup \textbf{brown sugar}. Return browned \textbf{sausage} to pot and stir to combine.
    
    \item Bring to a gentle simmer, then reduce heat to low. Simmer uncovered for \textit{2~hours}, stirring occasionally and scraping bottom to prevent sticking. Sauce should reduce and concentrate significantly.
    
    \item During final \textit{30~minutes}, add \textbf{lemon~juice}, and \textbf{chicken~stock} as needed if sauce becomes too thick. Taste and adjust with additional \textbf{brown~sugar} or \textbf{Italian~seasoning} as needed. 
    
    
    \item Serve immediately over pasta or cool completely before storing.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Large heavy-bottomed pot or Dutch oven (6-8 quart capacity)
    \item Sharp chef's knife and cutting board
    \item Large wooden spoon or spatula
    \item Slotted spoon for removing sausage
    \item Can opener
    \item Measuring cups and spoons
    \item Large bowl for crushed tomatoes
    \item Ladle for serving
    \item Timer for monitoring cook time
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Complete all vegetable prep before starting
    \item Open and crush \textbf{San~Marzano~tomatoes} by hand in bowl
    \item Have \textbf{wine} open and measured
    \item Pre-measure \textbf{Italian~seasoning} and \textbf{brown~sugar}
    \item Keep \textbf{chicken~stock} nearby for final adjustments
    \item Reserve \textbf{lemon~juice} for finishing
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use high-quality bulk \textbf{Italian~sausage} from butcher for best flavor
    \item San Marzano DOP tomatoes provide superior sweetness and acidity
    \item Crushing tomatoes by hand creates better texture than machine processing
    \item Use dry red wine you'd drink - \textbf{Merlot}, \textbf{Chianti}, or \textbf{Côtes~du~Rhône} work well
    \item \textbf{Italian~seasoning} should be basil and thyme heavy with oregano and touch of rosemary
    \item Fresh \textbf{lemon~juice} is essential for proper acid balance
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Don't skip browning the \textbf{sausage} - the fond creates essential flavor base
    \item Maintain gentle simmer throughout long cook to prevent scorching
    \item Stir occasionally and scrape bottom to prevent sticking
    \item Sauce should reduce by about one-third during \textit{2~hour} cook
    \item Taste and adjust seasoning progressively, not just at end
    \item Final consistency should coat pasta without being too thick
    \item Add \textbf{lemon~juice} off heat to preserve brightness
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Sauce improves with overnight rest - flavors meld beautifully
    \item Refrigerate up to \textit{5~days} or freeze up to \textit{3~months}
    \item Reheat gently, adding \textbf{chicken~stock} if needed to restore consistency
    \item Can double recipe easily for batch cooking
    \item Freeze in portion-sized containers for quick weeknight meals
    \item Add fresh \textbf{lemon~juice} when reheating for brightness
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve over \textbf{spaghetti}, \textbf{rigatoni}, or \textbf{penne} pasta
    \item Reserve pasta water to adjust sauce consistency if needed
    \item Garnish with fresh \textbf{basil}, \textbf{Parmesan}, and cracked pepper
    \item Pairs excellently with garlic bread and Caesar salad
    \item Makes enough sauce for \textit{1\nicefrac{1}{2}~pounds} of pasta
    \item Also excellent as base for lasagna or baked ziti
    \item Serve with robust red wine like \textbf{Chianti} or \textbf{Sangiovese}
\end{itemize}

\end{multicols}
}

\end{document}