\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Boeuf Bourguignon}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Chuck roast \dotfill 4 lbs. \\
    Thick-cut bacon \dotfill 8 oz. \\
    Cremini mushrooms \dotfill 16 oz. \\
    Pearl onions, frozen \dotfill 16 oz. \\
    Yellow onions \dotfill 2 large \\
    Carrots \dotfill 4 large \\
    Celery stalks \dotfill 3 \\
    Shallots \dotfill 2 medium \\
    Garlic cloves \dotfill 8 \\
    Burgundy wine \dotfill 750 ml \\
    Cognac \dotfill \nicefrac{1}{4} cup \\
    Beef Better Than Bouillon \dotfill 2 Tbsp. \\
    \columnbreak
    Water \dotfill 2 cups \\
    Tomato paste \dotfill 2 Tbsp. \\
    Unsalted butter \dotfill 6 Tbsp. \\
    All-purpose flour \dotfill \nicefrac{1}{3} cup \\
    Fresh thyme \dotfill 8 sprigs \\
    Fresh parsley \dotfill 1 bunch \\
    Bay leaves \dotfill 2 \\
    Black peppercorns \dotfill 1 Tbsp. \\
    MSG \dotfill \nicefrac{1}{4} tsp. \\
    Kosher salt \dotfill 2 Tbsp. \\
    Black pepper, ground \dotfill 1 Tbsp.
\end{multicols}

\section*{Directions}

\noindent
Salt \textbf{beef} \textit{24~hours} ahead ---
Bring \textbf{beef} to room temperature \textit{2~hours} before cooking ---
Preheat oven to \textit{300°F} ---
Cut \textbf{beef} into 2\nicefrac{1}{2}~inch pieces ---
Dice \textbf{bacon} into \nicefrac{1}{2}~inch lardons; set aside in \textit{Small Bowl~\#1} ---
Prepare mirepoix: dice \textbf{onions}, \textbf{carrots}, \textbf{celery}; combine in \textit{Large Bowl~\#1} ---
Mince \textbf{shallots}; set aside in \textit{Small Bowl~\#2} ---
Crush \textbf{garlic} cloves lightly; set aside in \textit{Small Bowl~\#3} ---
Quarter \textbf{mushrooms} if large; set aside in \textit{Medium Bowl~\#1} ---
Make bouquet garni with \textbf{thyme}, \textbf{parsley} stems, \textbf{bay leaves}, \textbf{peppercorns} ---
Dissolve \textbf{Better Than Bouillon} in \textit{hot} \textbf{water}; set aside in \textit{Medium Bowl~\#2}

\begin{enumerate}
    \item Start with cold Dutch oven. Add \textbf{bacon} (\textit{Small Bowl~\#1}), turn to medium-low heat, render until crisp (\textit{12-15~minutes}). Remove with slotted spoon and transfer to \textit{Medium Bowl~\#3}; set aside.
    
    \item Increase heat to medium-high. Working in batches, brown \textbf{beef} until deeply caramelized (\textit{4-5~minutes} per side). Transfer to \textit{Large Bowl~\#2}; set aside.
    
    \item Lower heat to medium. Add half the \textbf{wine}, scrape fond. Strain liquid into separate pot, reserve in \textit{Medium Bowl~\#4}.
    
    \item Return Dutch oven to medium heat. Add 2~Tbsp. \textbf{butter}, \textbf{onions}, \textbf{carrots}, \textbf{celery} (\textit{Large Bowl~\#1}), \textbf{shallots} (\textit{Small Bowl~\#2}), and \nicefrac{1}{4}~tsp. \textbf{MSG}. Cook until onions are translucent (\textit{8-10~minutes}).
    
    \item Add \textbf{garlic} (\textit{Small Bowl~\#3}), cook \textit{1~minute}. Add 2~Tbsp. \textbf{tomato paste}, cook until darkened (\textit{2-3~minutes}).
    
    \item Add \nicefrac{1}{4}~cup \textbf{cognac}, reduce until nearly dry. Add \nicefrac{1}{3}~cup \textbf{flour}, cook (\textit{2~minutes}).
    
    \item Return \textbf{beef} (\textit{Large Bowl~\#2}), \textbf{bacon} (\textit{Medium Bowl~\#3}), reserved wine liquid (\textit{Medium Bowl~\#4}), remaining \textbf{wine}, and \textbf{bouillon mixture} (\textit{Medium Bowl~\#2}). Add bouquet garni. Bring to simmer.
    
    \item Cover, transfer to oven. Braise until meat reaches \textit{195°F}, about \textit{2\nicefrac{1}{2}-3~hours}. Check liquid level hourly.
    
    \item Meanwhile, blanch \textbf{pearl onions} in boiling water (\textit{1~minute}). Shock in ice bath, peel; set aside in \textit{Small Bowl~\#4}.
    
    \item In large skillet, sauté \textbf{mushrooms} (\textit{Medium Bowl~\#1}) in 2~Tbsp. \textbf{butter} until golden (\textit{8-10~minutes}). Set aside in \textit{Medium Bowl~\#5}.
    
    \item Brown \textbf{pearl onions} (\textit{Small Bowl~\#4}) in same skillet with remaining 2~Tbsp. \textbf{butter} until caramelized (\textit{5-6~minutes}). Set aside in \textit{Small Bowl~\#4}.
    
    \item When meat is tender, remove from oven. Transfer \textbf{beef} pieces to \textit{Large Bowl~\#2}. Strain sauce into clean pot, pressing solids.
    
    \item Reduce sauce until slightly thickened. Meanwhile, make beurre manié: knead 2~Tbsp. each softened \textbf{butter} and \textbf{flour} in \textit{Small Bowl~\#5}.
    
    \item Whisk beurre manié (\textit{Small Bowl~\#5}) into simmering sauce in small pieces until desired consistency. Return \textbf{beef} (\textit{Large Bowl~\#2}), add \textbf{mushrooms} (\textit{Medium Bowl~\#5}) and \textbf{pearl onions} (\textit{Small Bowl~\#4}).
    
    \item Simmer gently \textit{5~minutes}. Adjust seasoning with \textbf{salt} and \textbf{pepper}. Rest \textit{20~minutes}.
    
    \item Garnish with chopped \textbf{parsley}. Serve with crusty bread or buttered egg noodles.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\footnotesize
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlength{\itemsep}{0pt}
\setlength{\parsep}{0pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 7-8 quart enameled cast iron Dutch oven
    \item 12-inch heavy-bottom skillet
    \item Fine-mesh strainer
    \item 2-quart saucepan (for reducing wine)
    \item Digital instant-read thermometer
    \item Kitchen twine and cheesecloth (for bouquet garni)
    \item Large mixing bowls (3-4)
    \item Heavy cutting board
    \item Sharp chef's knife
    \item Kitchen spider or slotted spoon
    \item Wooden spoons and whisks
    \item Measuring cups and spoons
    \item Large plate lined with paper towels
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Season \textbf{beef} \textit{24~hours} ahead, store uncovered in refrigerator
    \item Remove \textbf{beef} \textit{2~hours} before cooking
    \item Open \textbf{wine} to breathe \textit{1~hour} before cooking
    \item Prepare bouquet garni in cheesecloth, tie securely
    \item Cut all vegetables before beginning
    \item Have additional hot \textbf{stock} ready
    \item Soften butter for beurre manié ahead of time
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Choose well-marbled \textbf{chuck roast}, preferably center-cut
    \item Use young red Burgundy (Pinot Noir) or Côtes du Rhône
    \item Select slab \textbf{bacon} for even lardons
    \item \textbf{Better Than Bouillon} must be "Roasted Beef Base"
    \item European-style \textbf{butter} (82\% butterfat) preferred
    \item Fresh \textbf{herbs} only - dried will muddy the sauce
    \item Choose small \textbf{cremini mushrooms} for even cooking
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Cut \textbf{beef} against grain in equal sizes for even cooking
    \item Pat \textbf{beef} thoroughly dry before browning
    \item Cold start for \textbf{bacon} ensures proper rendering
    \item Never crowd pan when browning - pieces should not touch
    \item Dark fond is crucial - but watch carefully to prevent burning
    \item Skim surface fat during braising every \textit{30~minutes}
    \item Test several pieces of \textbf{meat} for doneness
    \item Sauce should coat the back of a spoon when finished
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Improves if made \textit{1-2~days} ahead
    \item Cool completely before refrigerating
    \item Remove solidified fat cap before reheating
    \item Reheat gently at \textit{300°F} for \textit{30-45~minutes}
    \item Add hot stock if needed during reheating
    \item Can freeze up to \textit{3~months} in airtight container
    \item Thaw completely in refrigerator before reheating
\end{itemize}

\subsection*{Troubleshooting}
\begin{itemize}
    \item If sauce is too thin: make additional beurre manié
    \item If sauce breaks: whisk in cold \textbf{butter} piece by piece
    \item If meat is tough: continue cooking, check every \textit{15~minutes}
    \item If fond is too dark: deglaze immediately with \textbf{wine}
    \item If sauce is too acidic: add a pinch of sugar
    \item If seasoning is flat: add \textbf{MSG} in small increments
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Rest \textit{20-30~minutes} before serving
    \item Traditional: egg noodles or pommes mousseline
    \item Crusty baguette for sauce
    \item Serve same \textbf{wine} used in cooking
    \item Garnish with fresh \textbf{parsley} and extra \textbf{pearl onions}
    \item Simple green salad with vinaigrette to balance
\end{itemize}

\end{multicols}
}

\end{document}