\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.5in,right=1.5in,top=1.5in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Breakfast Burritos}
\author{Patrick }
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Breakfast sausage \dotfill 16-24 oz. \\
    Bell pepper \dotfill 1 \\
    Onion \dotfill 1 \\
    Green chilis \dotfill 1 (6oz.) can \\
    Eggs \dotfill 12 \\
    Milk \dotfill 1 ½ cups \\
    \columnbreak
    Sour cream \dotfill ¾ cup \\
    Salt \dotfill 1 tsp. \\
    Black pepper \dotfill ½ tsp. \\
    Ground mustard \dotfill ¼ tsp. \\
    MSG \dotfill ¼ tsp. \\
    Cooking oil (or spray) \dotfill 1 tsp. \\
    Frozen tater tots \dotfill 30 oz. \\
    Tortillas, burrito size \dotfill 12-16 \\
    Shredded cheese \dotfill 3-4 cups
\end{multicols}

\section*{Directions}
\noindent
Preheat oven to 350°F --- Dice \textbf{bell peppers} and \textbf{onions} --- Drain \textbf{chilis}

\begin{enumerate}
    \item Cook the \textbf{breakfast sausage}, \textbf{bell peppers}, \textbf{onions}, and \textbf{chilis}, over medium heat, crumbling the sausage until cooked through. Drain grease.
    \item Whisk together the \textbf{eggs}, \textbf{milk}, \textbf{sour cream}, \textbf{salt}, \textbf{black pepper}, \textbf{ground mustard}, \textbf{MSG} and  until smooth.
    \item Lightly grease a 9”×13” baking pan with \textbf{oil or cooking spray}. Place the \textbf{tater tots} in the bottom of the pan.
    \item Sprinkle the cooked \textbf{sausage} mixture over the \textbf{tater tots} in the prepared pan. Pour the \textbf{egg} mixture evenly over the top. 
    \item Bake at 350°F for 30 minutes covered, then 30-45 minutes uncovered until set.
    \item If freezing, let the casserole cool to room temperature. Scoop about ½ cup of the casserole onto each \textbf{tortilla}, sprinkle with \textbf{cheese}, fold the sides, and roll up into a burrito.
    \item To freeze, wrap burritos in parchment paper or plastic wrap, and place in a freezer bag. Reheat in the microwave or oven as desired.
\end{enumerate}

\end{document}
