\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=0.5in,bottom=0.5in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Chicken-Broccoli-Rice Casserole}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Long-grain white rice \dotfill 2 cups \\
    Chicken breasts, cubed \dotfill 2 lbs \\
    Frozen mixed vegetables \dotfill 16 oz \\
    Canned sliced mushrooms \dotfill 4 oz \\
    Cream of chicken soup \dotfill 10 oz \\
    Sour cream \dotfill ½ cup \\
    Chicken broth \dotfill ¼ cup \\
    Cheddar cheese, shredded \dotfill 8 oz \\
    \columnbreak
    Parmesan cheese, grated \dotfill ½ cup \\
    Garlic powder \dotfill 2 tsp \\
    Onion powder \dotfill 2 tsp \\
    Smoked paprika \dotfill 1 tsp \\
    Hot paprika \dotfill ¼ tsp \\
    Salt \dotfill 1 tsp \\
    Black pepper \dotfill ½ tsp \\
    Olive oil \dotfill 2 Tbsp \\
    French fried onions \dotfill 1½ cups \\
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{375°F} ---
Grease a 9x13 inch baking dish ---
Drain \textbf{canned~mushrooms}

\begin{enumerate}
    \item Cook \textbf{rice}. Once done, fluff with a fork and set aside.

    \item In a large skillet, heat \textbf{olive~oil} over medium-high heat. Add cubed \textbf{chicken} and cook for \textit{5--7~minutes}, stirring occasionally, until lightly browned but not fully cooked. Remove from heat.

    \item In a large bowl, whisk together \textbf{cream~of~chicken~soup}, \textbf{sour~cream}, and \textbf{chicken~broth}. Add \textbf{garlic~powder}, \textbf{onion~powder}, \textbf{dried~thyme}, \textbf{salt}, and \textbf{black~pepper}. Mix well.

    \item Add the cooked \textbf{rice}, frozen \textbf{mixed~vegetables} (no need to thaw), drained \textbf{canned~mushrooms}, and partially cooked \textbf{chicken} to the bowl with the sauce. Gently fold everything together until well combined.

    \item Transfer half of the mixture to the prepared baking dish. Sprinkle with 1 cup of \textbf{cheddar~cheese}.

    \item Add the remaining mixture on top and sprinkle with the remaining \textbf{cheddar~cheese} and \textbf{Parmesan~cheese}.

    \item Top with \textbf{French~fried~onions}.

    \item Cover the dish with aluminum foil and bake for \textit{30~minutes}.

    \item Remove foil and bake for an additional \textit{10--15~minutes}, until the casserole is bubbly, the cheese is melted, and the French fried onions are golden brown.

    \item Remove from oven and let stand for \textit{5--10~minutes} before serving.
\end{enumerate}

\end{document}
