\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Chicken Broccoli Rice Casserole}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Rotisserie chicken meat \dotfill 2lb. \\
    Long-grain white rice \dotfill 2 cups \\
    Chicken broth \dotfill 4 cups \\
    Broccoli \dotfill 1 head \\
    Sharp cheddar \dotfill 8 oz. \\
    Cream cheese, softened \dotfill 6 oz. \\
    Onion, medium \dotfill 1 \\
    Garlic cloves \dotfill 6-8 \\
    Butter \dotfill 4½ Tbsp. \\
    Flour \dotfill ¼ cup \\
    Milk \dotfill 2 cups \\
    \columnbreak
    Mushrooms, canned \dotfill 8 oz. \\
    Sweet Corn, canned \dotfill 8 oz. \\
    Diced green chiles \dotfill 2 Tbsp. \\
    Dried rosemary \dotfill 1 tsp. \\
    Paprika \dotfill 1 tsp. \\
    MSG \dotfill ¼ tsp. \\
    Garlic powder \dotfill ½ tsp. \\
    Onion powder \dotfill ½ tsp. \\
    Ground nutmeg \dotfill ¼ tsp. \\
    Salt \dotfill 1 tsp. \\
    Black pepper \dotfill ½ tsp. \\
    Red pepper, crushed \dotfill ½ tsp.
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{375°F} ---
Soften \textbf{cream cheese} at room temperature ---
Grease a 9x13 inch baking dish with ½~Tbsp. butter ---
Debone bird by hand and dice meat ---
Shred \textbf{cheddar} ---
Dice \textbf{onion} ---
Mince \textbf{garlic} ---
Cut \textbf{broccoli} into florets ---
Drain \textbf{mushrooms}

\begin{enumerate}
    \item Cook \textbf{rice} al-dente using 2 cups \textbf{chicken broth} instead of water. Stop your rice cooker 10 minutes early.
    
    \item While rice cooks, bring a pot of salted water to boil. Blanch \textbf{broccoli florets} for \textit{2~minutes}, then immediately strain in a metal colander rinsing with cold water. Drain well.
    
    \item In a large saucepan, melt remaining \textbf{butter} over medium heat. Add diced \textbf{onion} and cook until translucent, about \textit{5~minutes}. Add minced \textbf{garlic} and \textbf{mushrooms}, cooking for another \textit{5~minutes}.
    
    \item Sprinkle \textbf{flour} over the butter mixture and cook, stirring constantly, for \textit{2~minutes}.
    
    \item Gradually whisk in \textbf{milk} and 2 cups \textbf{chicken~broth}. Add \textbf{cream~cheese} and stir until melted. Add \textbf{rosemary}, \textbf{paprika}, \textbf{MSG}, \textbf{garlic powder}, \textbf{onion~powder}, \textbf{nutmeg}, \textbf{salt},  \textbf{black~pepper}, and \textbf{red~pepper}. Simmer, stirring frequently, until sauce thickens, about \textit{5~minutes}.
    
    \item In a large bowl, combine cooked \textbf{rice}, blanched \textbf{broccoli}, diced \textbf{chicken}, \textbf{green chiles}, \textbf{corn}, and sauce. Mix well.
    
    \item Transfer mixture to prepared baking dish. Top with shredded \textbf{cheddar}.
    
    \item Bake for \textit{30~minutes} until bubbly and cheese is melted.
    
    \item Let stand for \textit{5-10~minutes} before serving.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Large saucepan for sauce
    \item Large mixing bowl (6+ quart)
    \item Box grater
    \item Colander
    \item Whisk
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Soften \textbf{cream cheese} for \textit{1~hour} before starting
    \item Debone chicken while cold for easier handling
    \item Have all measured ingredients grouped by cooking stage
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Pre-shredded cheese won't melt as smoothly as freshly grated
    \item Full-fat dairy prevents sauce from breaking
    \item Choose plain canned \textbf{mushrooms}, not seasoned varieties
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Cook \textbf{rice} slightly al dente - it will continue cooking in casserole
    \item Whisk continuously when adding liquids to prevent lumps
    \item If sauce seems too thick, thin with warm \textbf{broth}
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Can assemble \textit{24~hours} ahead
    \item Add ¼ cup extra \textbf{broth} if refrigerated before baking
    \item Freezes well for up to \textit{3~months}
    \item Thaw frozen casserole overnight in refrigerator
    \item Reheat covered at \textit{350°F} until hot throughout, about \textit{20~minutes}
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Try crushed crackers on top for crunch
\end{itemize}

\end{multicols}
}

\end{document}
