\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1in,right=1in,top=0.25in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Coq au Riesling}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Chicken thighs, bone-in \dotfill 2½-3 lbs \\
    Thick-cut bacon \dotfill 6 oz \\
    Riesling wine \dotfill 2 cups \\
    Leeks \dotfill 4 medium \\
    Cremini mushrooms \dotfill 8 oz \\
    Butter \dotfill ½ cup \\
    Garlic head \dotfill 1 whole \\
    \columnbreak
    Fresh thyme \dotfill 2 sprigs \\
    Fresh parsley \dotfill 2 sprigs \\
    Bay leaves \dotfill 2 \\
    Better than Bouillon, chicken \dotfill 1½ tsp \\
    Water \dotfill 1½ cups \\
    Heavy cream \dotfill ½ cup \\
    Egg yolk \dotfill 1 \\
    All-purpose flour \dotfill 1 Tbsp \\
    Salt and black pepper \dotfill to taste \\
\end{multicols}

\section*{Directions}

\noindent
Cut \textbf{garlic} head in half horizontally ---
Clean \textbf{leeks} thoroughly and slice into ½" rounds ---
Quarter \textbf{mushrooms} ---
Dice \textbf{thick-cut bacon} into ¼" pieces ---
Chop \textbf{parsley} for garnish ---
Mix \textbf{Better than Bouillon} with \textbf{hot water} until dissolved.

\begin{enumerate}
    \item In a large bowl, combine \textbf{chicken thighs}, halved \textbf{garlic head}, 1 sprig \textbf{thyme}, 1 sprig \textbf{parsley}, 1 \textbf{bay leaf}, and 1 tsp \textbf{salt}. Pour in \textbf{Riesling}. Cover and refrigerate for up to \textit{12 hours}.

    \item When ready to cook, remove \textbf{chicken} from marinade and pat dry. Reserve the \textbf{wine marinade}. 
    
    \item Melt ¼ of the \textbf{butter} in a large Dutch oven over medium-high heat. Cook diced \textbf{bacon} until golden. Remove with a slotted spoon.

    \item Add another ¼ of \textbf{butter}, then cook \textbf{leeks} with a pinch of \textbf{salt} until soft, about \textit{5 minutes}. Remove to bacon bowl.
    
    \item Add another ¼ of \textbf{butter} and cook \textbf{mushrooms} until golden. Remove to same bowl.

    \item Melt remaining \textbf{butter}. Season \textbf{chicken} with \textbf{salt} and \textbf{pepper}, then brown on all sides until deep golden, about \textit{8-10 minutes}.

    \item Remove \textbf{chicken}. Lower heat and stir \textbf{flour} into pan drippings. Cook for \textit{2 minutes}, then add reserved \textbf{wine marinade} and \textbf{bouillon mixture}, scraping bottom of pan.

    \item Return \textbf{chicken} to pot. Simmer covered for \textit{90 minutes}, until meat is very tender.

    \item Remove \textbf{chicken}. Whisk \textbf{cream} and \textbf{egg yolk} in a small bowl. Off heat, whisk into sauce. Return to low heat and cook until thickened.

    \item Add back \textbf{bacon}, \textbf{leeks}, \textbf{mushrooms}, and \textbf{chicken}. Warm through gently. Garnish with chopped \textbf{parsley}.
\end{enumerate}

\end{document}
