\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Chicken Broccoli Rice Casserole (Gluten-Free)}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Long-grain white rice \dotfill 2 cups \\
    Chicken broth (for rice) \dotfill 3 cups \\
    Cooked chicken, diced \dotfill 1 lb. \\
    Broccoli florets \dotfill 8 oz. \\
    Sharp cheddar cheese \dotfill 8 oz. \\
    Cream cheese, softened \dotfill 6 oz. \\
    Onion, medium \dotfill 1 \\
    Garlic cloves \dotfill 6-8 \\
    Butter \dotfill 4 Tbsp. \\
    Gluten-free flour \dotfill ¼ cup \\
    Milk \dotfill 2 cups \\
    \columnbreak
    Chicken broth \dotfill 1 cup \\
    Canned mushrooms \dotfill 8 oz. can \\
    Diced green chiles \dotfill 4 oz. can \\
    Dried thyme \dotfill 1 tsp. \\
    Paprika \dotfill 1 tsp. \\
    MSG \dotfill ½ tsp. \\
    Garlic powder \dotfill ½ tsp. \\
    Onion powder \dotfill ½ tsp. \\
    Ground nutmeg \dotfill ¼ tsp. \\
    Salt \dotfill 1 tsp. \\
    Black pepper \dotfill ½ tsp. \\
\end{multicols}

\section*{Directions}

\noindent
Preheat oven to \textit{350°F} ---
Grease a 9x13 inch baking dish ---
Shred \textbf{sharp cheddar} ---
Dice \textbf{onion} ---
Mince \textbf{garlic} ---
Cut \textbf{broccoli} into florets ---
Drain \textbf{mushrooms} ---
Soften \textbf{cream cheese} at room temperature

\begin{enumerate}
    \item Cook \textbf{rice} using \textbf{chicken broth} instead of water according to package directions.
    
    \item While rice cooks, bring a pot of salted water to boil. Blanch \textbf{broccoli florets} for \textit{2~minutes}, then immediately transfer to an ice bath. Drain well.
    
    \item In a large saucepan, melt \textbf{butter} over medium heat. Add diced \textbf{onion} and cook until translucent, about \textit{5~minutes}. Add minced \textbf{garlic} and drained \textbf{mushrooms}, cooking for another \textit{2-3~minutes}.
    
    \item Sprinkle \textbf{gluten-free flour} over the butter mixture and cook, stirring constantly, for \textit{1-2~minutes}.
    
    \item Gradually whisk in \textbf{milk} and \textbf{chicken broth}. Add \textbf{cream cheese} and stir until melted. Add \textbf{thyme}, \textbf{paprika}, \textbf{MSG}, \textbf{garlic powder}, \textbf{onion powder}, \textbf{nutmeg}, \textbf{salt}, and \textbf{pepper}. Simmer, stirring frequently, until sauce thickens, about \textit{5~minutes}.
    
    \item In a large bowl, combine cooked \textbf{rice}, blanched \textbf{broccoli}, diced \textbf{chicken}, \textbf{green chiles}, and sauce. Mix well.
    
    \item Transfer mixture to prepared baking dish. Top with shredded \textbf{sharp cheddar}.
    
    \item Bake for \textit{25-30~minutes} until bubbly and cheese is melted.
    
    \item Let stand for \textit{5-10~minutes} before serving.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 9x13 inch baking dish
    \item Large saucepan for sauce
    \item Medium pot for rice
    \item Large pot for blanching broccoli
    \item Large mixing bowl
    \item Colander or strainer
    \item Box grater for cheese
    \item Whisk
    \item Measuring cups and spoons
    \item Cutting board and sharp knife
    \item Wooden spoon or spatula
    \item Bowl for ice bath
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Bring \textbf{cream cheese} to room temperature \textit{1~hour} before starting
    \item Dice chicken if not already prepared
    \item Cut broccoli into uniform florets for even cooking
    \item Measure all ingredients before starting the sauce
    \item Have ice bath ready before blanching \textbf{broccoli}
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Use a 1:1 gluten-free flour blend for best results
    \item Sharp or extra-sharp cheddar provides the best flavor
    \item Fresh broccoli is preferred over frozen for better texture
    \item Rotisserie chicken works well for convenience
    \item Full-fat dairy products yield the creamiest sauce
    \item Use mild \textbf{green chiles} for flavor without heat
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Don't skip blanching the \textbf{broccoli} - it ensures perfect texture
    \item Cook \textbf{rice} slightly al dente as it will continue cooking in the casserole
    \item Whisk sauce continuously to prevent lumps
    \item Let \textbf{cream cheese} fully soften for smooth incorporation
    \item If sauce is too thick, thin with additional warm \textbf{broth}
    \item Taste and adjust seasonings before adding to casserole
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Can be assembled up to \textit{24~hours} ahead and refrigerated
    \item If made ahead, bring to room temperature for \textit{30~minutes} before baking
    \item Add extra \textbf{broth} if mixture seems dry after refrigeration
    \item Leftovers keep for \textit{3-4~days} in refrigerator
    \item Reheat covered at \textit{350°F} until warm, about \textit{20~minutes}
    \item Can be frozen for up to \textit{3~months}; thaw overnight in refrigerator
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve with a crisp green salad
    \item Top with extra shredded \textbf{cheese} if desired
    \item Garnish with fresh parsley or chives
    \item Add crushed gluten-free crackers on top for extra crunch
    \item Pairs well with additional steamed vegetables
    \item Consider serving with gluten-free garlic bread
\end{itemize}

\end{multicols}
}

\end{document}
