\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Jerk Chicken Rasta Pasta}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Boneless chicken thighs \dotfill 2 lbs. \\
    Jerk seasoning \dotfill 5 Tbsp. \\
    Better Than Bouillon chicken \dotfill 1 Tbsp. \\
    Water \dotfill 1 cup \\
    Onion, small \dotfill 1 \\
    Garlic cloves \dotfill 7 \\
    Fresh thyme sprigs \dotfill 2 \\
    Penne pasta \dotfill 16 oz. \\
    Red bell pepper \dotfill 1 \\
    \columnbreak
    Yellow bell pepper \dotfill 1 \\
    Green bell pepper \dotfill 1 \\
    Green onions \dotfill 1 bunch \\
    Vegetable oil \dotfill 2 Tbsp. \\
    Heavy cream \dotfill \nicefrac{1}{2} cup \\
    Parmesan cheese \dotfill \nicefrac{1}{2} cup \\
    Cilantro \dotfill \nicefrac{1}{4} cup \\
    Salt \dotfill to taste \\
    Black pepper \dotfill to taste \\
\end{multicols}

\section*{Directions}

\noindent
Preheat Instant Pot ---
Quarter \textbf{onion}; set aside in \textit{Small Bowl~\#1} ---
Smash 4 \textbf{garlic cloves}; set aside in \textit{Small Bowl~\#2} ---
Mince remaining 3 \textbf{garlic cloves}; set aside in \textit{Small Bowl~\#3} ---
Slice \textbf{bell peppers} into strips; combine in \textit{Medium Bowl~\#1} ---
Slice \textbf{green onions}; set aside in \textit{Small Bowl~\#4} ---
Grate \textbf{Parmesan cheese}; set aside in \textit{Small Bowl~\#5} ---
Chop \textbf{cilantro} roughly; set aside in \textit{Small Bowl~\#6}

\begin{enumerate}
    \item Coat \textbf{chicken thighs} thoroughly with 3 Tbsp. \textbf{jerk seasoning}, rubbing it in well.
    
    \item Add \textbf{water} and \textbf{Better Than Bouillon} to Instant Pot and stir to combine.
    
    \item Place seasoned \textbf{chicken} in the broth and add quartered \textbf{onion}, 4 smashed \textbf{garlic cloves}, and \textbf{thyme} sprigs.
    
    \item Seal the Instant Pot and cook on High Pressure for \textit{15~minutes}, followed by a \textit{10-minute} natural release.
    
    \item Remove \textbf{chicken} to \textit{Large Bowl~\#1} and shred using two forks. Reserve \nicefrac{1}{4}~cup of the cooking broth in \textit{Small Bowl~\#7} and stir 2-3~Tbsp. back into the shredded \textbf{chicken} (\textit{Large Bowl~\#1}) to keep it moist.
    
    \item Cook \textbf{pasta} in salted water according to package directions until al dente. Drain and set aside in \textit{Large Bowl~\#2}.
    
    \item In a large, heavy-bottomed pot, heat 2~Tbsp. \textbf{vegetable oil} over medium-high heat. Add \textbf{bell peppers} (\textit{Medium Bowl~\#1}) and half the \textbf{green onions} (\textit{Small Bowl~\#4}), sautéing for \textit{3-4~minutes} until peppers begin to soften but remain crisp.
    
    \item Add minced \textbf{garlic} (\textit{Small Bowl~\#3}) and cook for \textit{30~seconds} until fragrant.
    
    \item Sprinkle in remaining 2~Tbsp. \textbf{jerk seasoning} and stir to coat vegetables.
    
    \item Pour in the reserved \textbf{chicken broth} (\nicefrac{1}{4}~cup, \textit{Small Bowl~\#7}) and \nicefrac{1}{2}~cup \textbf{heavy cream}. Bring to a simmer.
    
    \item Reduce heat to medium-low and let sauce simmer for \textit{3-4~minutes} until it begins to thicken.
    
    \item Stir in the \textbf{Parmesan cheese} (\nicefrac{1}{2}~cup, \textit{Small Bowl~\#5}) until melted and sauce is smooth.
    
    \item Add shredded \textbf{jerk chicken} (\textit{Large Bowl~\#1}) and cooked \textbf{pasta} (\textit{Large Bowl~\#2}), tossing to coat evenly with the sauce. Season with \textbf{salt} and \textbf{black pepper} to taste.
    
    \item Serve immediately, garnished with remaining \textbf{green onions} (\textit{Small Bowl~\#4}) and chopped \textbf{cilantro} (\textit{Small Bowl~\#6}).
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Instant Pot or pressure cooker
    \item Large pasta pot (6-8 quart)
    \item Colander
    \item Large, heavy-bottomed pot or Dutch oven
    \item Wooden spoon or silicone spatula
    \item Measuring cups and spoons
    \item Sharp chef's knife
    \item Cutting board
    \item Box grater or microplane for cheese
    \item Two forks for shredding chicken
    \item Medium bowl for shredded chicken
    \item Small bowl for reserved broth
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Measure all seasonings and spices before beginning
    \item Allow heavy cream to come to room temperature
    \item Prepare all vegetables before starting to cook
    \item Grate cheese while chicken cooks in Instant Pot
    \item Have all ingredients within arm's reach before beginning sauce
    \item Keep pasta water heating while preparing the chicken
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Boneless chicken thighs provide more flavor and moisture than breast meat
    \item Store-bought jerk seasoning works well, but use a high-quality brand for authentic flavor
    \item For homemade jerk seasoning, combine allspice, thyme, cayenne, garlic powder, onion powder, cinnamon, nutmeg, brown sugar, and salt
    \item Freshly grated Parmesan is crucial - pre-shredded cheese often contains anti-caking agents
    \item For extra heat, add 1-2 teaspoons of minced scotch bonnet or habanero pepper
    \item Bell peppers can be substituted with poblano for a slightly spicier version
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Allow a full natural release if time permits - it keeps the chicken more tender
    \item Reserve more cooking broth than called for in case the sauce needs thinning
    \item Don't overcook the pasta - it will continue to absorb liquid in the sauce
    \item For bell peppers, aim for softened but still slightly crisp for best texture
    \item If sauce becomes too thick, add a splash of reserved cooking broth
    \item If sauce is too thin, simmer a few extra minutes before adding pasta
    \item Keep pasta very al dente as it will continue cooking in the hot sauce
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Chicken can be prepared up to \textit{2~days} ahead and refrigerated
    \item Complete dish keeps well refrigerated for up to \textit{3~days}
    \item When reheating, add a splash of chicken broth or cream to revive the sauce
    \item Reheat gently on stovetop over medium-low heat
    \item Microwave reheating works but may cause pasta to become slightly rubbery
    \item Freeze portions without pasta, then prepare fresh pasta when reheating
    \item Garnish with fresh cilantro only just before serving
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve with fried plantains for an authentic Caribbean pairing
    \item A simple green salad with lime vinaigrette balances the rich pasta
    \item Garlic bread made with Caribbean-style butter is an excellent side
    \item For a complete meal, add a tropical fruit salad as a refreshing dessert
    \item Offer extra jerk seasoning at the table for those who prefer more heat
    \item Jamaican Red Stripe beer or a fruity rum punch complement the flavors
    \item For a colorful presentation, serve in a large white bowl to highlight the vibrant peppers
\end{itemize}

\end{multicols}
}

\end{document}