\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.2,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Basic Rice (Rice Maker)}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\noindent
    Long grain white rice \dotfill 3 cups \\
    Hot water \dotfill 3 cups \\
    Better Than Bouillon - Chicken \dotfill 1 Tbsp. \\
    Bay leaf \dotfill 1 \\
    Butter \dotfill \nicefrac{1}{2} Tbsp. \\

\section*{Directions}

\noindent
Wash \textbf{rice} thoroughly ---
Prepare \textbf{stock} with \textbf{Better Than Bouillon}

\begin{enumerate}
    \item Wash \textbf{rice} thoroughly: Place \textbf{rice} in a fine-mesh strainer or bowl. Rinse under cold running water, gently agitating with your fingers, until the water runs clear (typically \textit{3-4~rinses}). Drain well.
    
    \item Combine \textbf{hot water} and \textbf{Better Than Bouillon} in a measuring cup, stirring to dissolve completely.
    
    \item Transfer washed \textbf{rice} to rice maker pot. Add prepared \textbf{stock} and \textbf{bay leaf}.
    
    \item Cook according to rice maker instructions (long grain white rice setting).
    
    \item Once cooking is complete, let rice rest for \textit{5~minutes} before opening.
    
    \item Open rice maker, remove \textbf{bay leaf}, and gently fluff rice with a fork or rice paddle.
    
    \item Add \textbf{butter} and gently fold into rice until evenly distributed. Serve immediately.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item Rice maker
    \item Fine-mesh strainer or large bowl
    \item Measuring cups and spoons
    \item Large measuring cup or bowl (for stock preparation)
    \item Rice paddle or fork (for fluffing)
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item Measure \textbf{rice}
    \item Measure \textbf{hot water} and \textbf{Better Than Bouillon}
    \item Have \textbf{bay leaf} ready
    \item Have \textbf{butter} at room temperature for easier incorporation
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Long-grain white rice works best for this method
    \item Thorough washing removes excess starch and prevents gummy texture
    \item \textbf{Better Than Bouillon} adds depth without overwhelming the rice
    \item Quality \textbf{butter} makes a noticeable difference in final flavor
    \item \textbf{Bay leaf} should be removed before serving
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Ensure \textbf{Better Than Bouillon} is fully dissolved before adding to rice maker
    \item Don't skip the washing step - it's essential for proper texture
    \item Let rice rest after cooking to allow steam to finish the process
    \item Fluff rice gently to avoid breaking grains
    \item Add \textbf{butter} while rice is still hot for best incorporation
    \item If rice seems too wet, let it sit with lid open for a few minutes
    \item If rice seems too dry, add a tablespoon of hot water and fluff again
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item Cooked \textbf{rice} keeps refrigerated for \textit{3-4~days}
    \item Reheat gently with a splash of water or broth to restore moisture
    \item Freeze cooked \textbf{rice} for up to \textit{2~months}
    \item Cool to room temperature before refrigerating
    \item Store in airtight container
    \item Label container with date
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve as side dish with any protein
    \item Use as base for grain bowls and stir-fries
    \item Perfect accompaniment to saucy dishes
    \item Use leftover rice for fried rice (best with day-old rice)
    \item Add to soups and casseroles
    \item Reheat gently with additional broth for extra flavor
\end{itemize}

\end{multicols}
}

\end{document}

