\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.4,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Italian Sausage Soup •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Sweet Italian sausage \dotfill 1 lb \\
    Hot Italian sausage \dotfill 1 lb \\
    Onion, large \dotfill 1 \\
    Garlic bulbs, minced \dotfill 2 \\
    Carrots, chopped \dotfill 3 \\
    Celery stalks, chopped \dotfill 3 \\
    Russet potatoes, chopped \dotfill 3 \\
    Zucchini, chopped \dotfill 1 \\
    Frozen vegetables (stir fry mix) \dotfill 1 lb \\
    \columnbreak
    Mushrooms, sliced \dotfill 12 oz. can \\
    Tomato sauce, unsalted \dotfill 12 oz. can \\
    Diced tomatoes w/basil \& garlic \dotfill 24 oz. can \\
    Chicken broth \dotfill 12-14 cups \\
    Italian herb mix \dotfill 1 tsp \\
    Basil \dotfill 1 tsp \\
    Parsley \dotfill 3 Tbsp \\
    Bay leaves \dotfill 3 \\
    Oregano \dotfill \nicefrac{1}{2} tsp. \\
    Sugar \dotfill 1 Tbsp \\
    Onion salt \dotfill 1 tsp \\
    MSG \textit{(optional)} \dotfill 1 tsp
\end{multicols}

\section*{Directions}

\noindent
Chop \textbf{onion}, \textbf{carrots}, \textbf{celery}, \textbf{potatoes}, and \textbf{zucchini}; combine in \textit{Large Bowl~\#1} ---
Mince \textbf{garlic}; set aside in \textit{Small Bowl~\#1} ---
Drain \textbf{mushrooms}; set aside in \textit{Medium Bowl~\#1}

\begin{enumerate}
    \item Brown 1~lb. \textbf{sweet Italian sausage} and 1~lb. \textbf{hot Italian sausage} into small chunks. Transfer to \textit{Medium Bowl~\#2}; set aside.
    \item Combine all ingredients in a large stock pot: browned \textbf{sausage} (\textit{Medium Bowl~\#2}), \textbf{onion}, \textbf{carrots}, \textbf{celery}, \textbf{potatoes}, and \textbf{zucchini} (\textit{Large Bowl~\#1}), \textbf{garlic} (\textit{Small Bowl~\#1}), 1~lb. \textbf{frozen vegetables}, \textbf{mushrooms} (\textit{Medium Bowl~\#1}), 12~oz. \textbf{tomato sauce}, 24~oz. \textbf{diced tomatoes}, 12-14~cups \textbf{chicken broth}, 1~tsp. \textbf{Italian herb mix}, 1~tsp. \textbf{basil}, 3~Tbsp. \textbf{parsley}, 3~ \textbf{bay leaves}, \nicefrac{1}{2}~tsp. \textbf{oregano}, 1~Tbsp. \textbf{sugar}, 1~tsp. \textbf{onion salt}, and 1~tsp. \textbf{MSG} (optional).
    \item Bring to a boil, reduce heat and simmer covered for \textit{30~minutes}.
    \item Stir occasionally and vigorously to thicken broth.
    \item For canning: process at \textit{15~pounds} for \textit{90~minutes}.
\end{enumerate}

\noindent
\textit{Add 1-2 cups of water per quart when reheating.}

\end{document}
