\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}

\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Berbere Spice Blend}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Sweet paprika \dotfill \nicefrac{1}{3} cup \\
    Cayenne pepper \dotfill 2\nicefrac{1}{2} Tbsp. \\
    Fenugreek seeds \dotfill 3 Tbsp. \\
    Coriander seeds \dotfill 2 Tbsp. \\
    Cumin seeds \dotfill 1\nicefrac{1}{2} Tbsp. \\
    Black peppercorns \dotfill 2 tsp. \\
    \columnbreak
    Allspice berries \dotfill 1 tsp. \\
    Ground cardamom \dotfill 1\nicefrac{1}{2} tsp. \\
    Ground cinnamon \dotfill 1 Tbsp. \\
    Ground ginger \dotfill 2 tsp. \\
    Ground turmeric \dotfill 1\nicefrac{1}{2} tsp. \\
    Ground cloves \dotfill \nicefrac{1}{2} tsp. \\
    Dried thyme \dotfill \nicefrac{1}{2} tsp. \\
\end{multicols}

\section*{Directions}

\noindent
Yield: approximately 1~cup

\begin{enumerate}
    \item Toast \textbf{fenugreek~seeds} in a dry skillet over medium-low heat, stirring constantly, for \textit{2-3~minutes} until fragrant and darkened one shade. Remove immediately when nutty, maple-like aroma develops. Transfer to a plate to cool.
    
    \item Toast \textbf{coriander~seeds} in the same skillet over medium heat, stirring frequently, for \textit{3-4~minutes} until fragrant and slightly darker. Transfer to cool.
    
    \item Toast \textbf{cumin~seeds}, \textbf{black~peppercorns}, and \textbf{allspice~berries} together over medium heat, stirring constantly, for \textit{2-3~minutes} until \textbf{cumin} becomes fragrant and darkens slightly. Transfer to cool.
    
    \item Let all toasted spices cool for \textit{5~minutes}. Grind each group separately in a spice grinder or mortar and pestle to a fine powder. \textbf{Fenugreek} is particularly hard—grind until no large pieces remain.
    
    \item In a medium bowl, combine all ground toasted spices with \textbf{sweet~paprika}, \textbf{cayenne~pepper}, \textbf{ground~cardamom}, \textbf{ground~cinnamon}, \textbf{ground~ginger}, \textbf{ground~turmeric}, \textbf{ground~cloves}, and \textbf{dried~thyme}.
    
    \item Whisk thoroughly for \textit{2-3~minutes} to ensure even distribution of all spices. Optionally sift for ultra-fine texture.
    
    \item Store in an airtight container in a cool, dark place. Peak flavor within \textit{2-3~months}, still good for \textit{6~months}. Flavor mellows and marries over the first week.
\end{enumerate}

\subsection*{Usage Notes}

\noindent
For stews and braises, use 2-3~Tbsp. per pound of meat. Bloom \textbf{berbere} in oil or butter over medium heat for \textit{1-2~minutes} before adding liquids to fully develop aromatic compounds. The spices require fat and time to release their complete flavor complexity.

\end{document}