\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage[left=1.4in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}

\title{Raspberry Swirl Lemon Bars (GF) •}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Fresh raspberries \dotfill 1\nicefrac{1}{2} cups \\
    Granulated sugar \dotfill 1 cup \\
    BRM 1:1 Baking Flour \dotfill 1\nicefrac{1}{4} cups \\
    Almond flour, finely ground \dotfill 3 Tbsp. \\
    Cornstarch \dotfill 3 Tbsp. + 1 tsp. \\
    Powdered sugar \dotfill \nicefrac{1}{2} cup \\
    \columnbreak
    Kerrygold butter \dotfill 16 Tbsp. \\
    Meyer lemons \dotfill 3 \\
    Mexican vanilla \dotfill \nicefrac{1}{2} tsp. \\
    Eggs \dotfill 3 \\
    Egg yolk \dotfill 1 \\
    TrueLemon powder \dotfill 1-2 tsp. \\
    Salt \dotfill \nicefrac{3}{4} tsp. \\
    Powdered sugar \dotfill for dusting \\
    Flaky salt \dotfill for sprinkling \\
\end{multicols}

\section*{Raspberry Reduction}

\noindent
Zest all 3 \textbf{Meyer lemons}; set aside zest from 1~lemon in \textit{Small Bowl~\#1} (for crust) and zest from 2~lemons in \textit{Small Bowl~\#2} (for curd) ---
Juice all 3 \textbf{lemons} to yield \nicefrac{1}{2}~cup + 2~tsp. juice; reserve 2~tsp. for reduction and \nicefrac{1}{2}~cup in \textit{Small Bowl~\#3} (for curd) ---
Cool reduction to room temperature before using ---
Transfer to piping bag or squeeze bottle with small round tip

\begin{enumerate}
    \item Combine 1\nicefrac{1}{2}~cups \textbf{fresh raspberries}, \nicefrac{1}{4}~cup \textbf{granulated sugar}, 2~tsp. \textbf{lemon juice}, and pinch of \textbf{salt} in a small saucepan. Bring to a simmer over medium heat, crushing \textbf{berries} with a wooden spoon as they soften. Cook for \textit{3-4~minutes} until berries have broken down completely.
    
    \item Press mixture through a fine-mesh sieve into \textit{Small Bowl~\#4}, using a silicone spatula to extract all liquid and leave seeds behind. Discard seeds. You should have about \nicefrac{3}{4}~cup strained raspberry liquid.
    
    \item Return strained liquid to the saucepan. Mix 1~tsp. \textbf{cornstarch} with 1~tsp. cold water in a small cup until smooth. Whisk cornstarch slurry into \textbf{raspberry liquid}.
    
    \item Simmer over medium-low heat, stirring frequently, until mixture is reduced by half and has thickened to a honey-like consistency, about \textit{8-10~minutes}. The reduction should coat the back of a spoon thickly and mound slightly when dripped. It will thicken further as it cools.
    
    \item Transfer to \textit{Small Bowl~\#5} and let cool to room temperature, about \textit{30~minutes}. Stir occasionally to prevent skin formation. Once cooled, transfer to a piping bag or squeeze bottle with a small round tip. Set aside until ready to use.
\end{enumerate}

\section*{Shortbread Crust}

\noindent
Preheat oven to \textit{350°F} ---
Line 8~inch×8~inch pan with parchment paper, leaving overhang ---
Bring 10~Tbsp. \textbf{butter} to room temperature

\begin{enumerate}
    \item In \textit{Medium Bowl~\#1}, whisk together 1\nicefrac{1}{4}~cups \textbf{gluten free flour}, 3~Tbsp. \textbf{almond flour}, 2~Tbsp. \textbf{cornstarch}, \nicefrac{1}{2}~cup \textbf{powdered sugar}, and \nicefrac{1}{4}~tsp. \textbf{salt}. Add 10~Tbsp. softened \textbf{butter}, \textbf{lemon zest} (\textit{Small Bowl~\#1}), and \nicefrac{1}{2}~tsp. \textbf{vanilla extract}. Mix with a fork or your hands until mixture forms clumps and holds together when pressed.
    
    \item Press dough evenly into prepared pan, creating a uniform \nicefrac{1}{2}~inch thick layer. Use the bottom of a measuring cup to compact and smooth the surface. Dock the crust all over with a fork.
    
    \item Bake at \textit{350°F} for \textit{20-25~minutes} until edges are golden brown and center is set. Remove from oven and reduce temperature to \textit{325°F}.
\end{enumerate}

\section*{Lemon Curd}

\noindent
Cut 6~Tbsp. \textbf{butter} into tablespoon pieces; set aside in \textit{Small Bowl~\#6}

\begin{enumerate}
    \item While crust bakes, whisk together \nicefrac{2}{3}~cup \textbf{granulated sugar} and 1~tsp. \textbf{cornstarch} in a medium saucepan. Add \textbf{eggs} and \textbf{egg yolk}, whisking until smooth.
    
    \item Add \textbf{lemon juice} (\nicefrac{1}{2}~cup, \textit{Small Bowl~\#3}), \textbf{lemon zest} (\textit{Small Bowl~\#2}), 1-2~tsp. \textbf{TrueLemon powder}, and \nicefrac{1}{4}~tsp. \textbf{salt}. Whisk to combine.
    
    \item Cook over medium-low heat, stirring constantly with a silicone spatula or wooden spoon, scraping the bottom and sides of the pan. Cook until mixture thickens noticeably and reaches \textit{170°F}, about \textit{8-10~minutes}. The curd should coat the back of a spoon and leave a clear trail when you draw your finger through it.
    
    \item Remove from heat and immediately stir in 6~Tbsp. \textbf{butter} (\textit{Small Bowl~\#6}), one piece at a time, until fully incorporated and smooth.
    
    \item Strain the hot curd through a fine-mesh sieve into \textit{Small Bowl~\#7} to remove \textbf{zest} bits and any cooked egg pieces.
\end{enumerate}

\newpage

\section*{Assembly and Baking}

\begin{enumerate}
    \item Pour strained curd onto the hot pre-baked crust, spreading gently to edges if needed.
    
    \item Immediately pipe \textbf{raspberry reduction} (\textit{Small Bowl~\#5}) in desired pattern on the surface of the \textbf{lemon curd}. Optionally drag a toothpick through the lines to create a marbled effect.
    
    \item Bake at \textit{325°F} for \textit{15-18~minutes} until filling is set but still jiggles slightly in the center when gently shaken. The \textbf{raspberry reduction} will set into the curd, creating a beautiful burgundy accent.
\end{enumerate}

\section*{Finishing}

\begin{enumerate}
    \item Cool completely in the pan on a wire rack for \textit{1~hour}, then refrigerate for at least \textit{3~hours} or overnight.
    
    \item Use parchment overhang to lift bars from pan. Cut into 16 squares using a sharp knife, wiping blade clean between cuts.
    
    \item Just before serving, dust moderately with \textbf{powdered sugar} and sprinkle lightly with \textbf{flaky sea salt}.
\end{enumerate}

\newpage

% Begin compact two-column layout
{\small
\setlength{\columnsep}{20pt}
\setlength{\multicolsep}{6pt}
\begin{multicols}{2}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\subsection*{Equipment Required}
\begin{itemize}
    \item 8x8 inch baking pan
    \item Parchment paper
    \item Small saucepan (1-quart capacity, for raspberry reduction)
    \item Medium saucepan (2-quart capacity, for lemon curd)
    \item Medium mixing bowl (for crust)
    \item Fine-mesh sieve or strainer (for straining raspberries and lemon curd)
    \item Piping bag or squeeze bottle with small round tip
    \item Silicone spatula or wooden spoon
    \item Whisk
    \item Measuring cups and spoons
    \item Microplane or fine grater (for zest)
    \item Citrus juicer or reamer (for juicing lemons)
    \item Fork (for docking crust)
    \item Instant-read thermometer (optional but helpful)
    \item Toothpick (optional, for swirling)
    \item Sharp knife for cutting
    \item Wire cooling rack
\end{itemize}

\subsection*{Mise en Place}
\begin{itemize}
    \item \textit{Small Bowl~\#1} --- lemon zest from 1 lemon (for crust)
    \item \textit{Small Bowl~\#2} --- lemon zest from 2 lemons (for curd)
    \item \textit{Small Bowl~\#3} --- lemon juice (\nicefrac{1}{2}~cup from 3 lemons, for curd)
    \item \textit{Small Bowl~\#4} --- strained raspberry liquid (about \nicefrac{3}{4}~cup)
    \item \textit{Small Bowl~\#5} --- cooled raspberry reduction in piping bag (ready to pipe)
    \item \textit{Small Bowl~\#6} --- 6~Tbsp. butter cut into pieces (for curd)
    \item \textit{Small Bowl~\#7} --- strained lemon curd (ready to pour)
    \item \textit{Medium Bowl~\#1} --- crust dry ingredients mixed with butter
    \item Zest all \textbf{Meyer lemons} before juicing (zest 1 for crust, zest 2 for curd, then juice all 3 for \nicefrac{1}{2}~cup + 2~tsp.)
    \item Reserve 2~tsp. \textbf{lemon juice} for raspberry reduction; remaining \nicefrac{1}{2}~cup goes in \textit{Small Bowl~\#3}
    \item Make \textbf{raspberry reduction} first; allow \textit{30~minutes} to cool to room temperature
    \item Bring 10~Tbsp. \textbf{butter} to room temperature for crust (\textit{1~hour})
    \item Line pan with parchment before starting
    \item Have all ingredients measured and ready
    \item Set up fine-mesh sieve over bowl for straining lemon curd
    \item Prepare piping bag or squeeze bottle with small round tip for raspberry reduction
\end{itemize}

\subsection*{Ingredient Tips}
\begin{itemize}
    \item Fresh \textbf{raspberries} should be ripe but not mushy; frozen raspberries work in a pinch but yield slightly more liquid
    \item Bob's Red Mill 1:1 G.F. flour works best; other blends may need adjustment
    \item \textbf{Almond flour} should be finely ground (blanched almond flour, not almond meal)
    \item European-style \textbf{butter} (Kerrygold, Plugrá) has higher fat content and richer flavor
    \item Use fresh \textbf{Meyer lemons}; zest before juicing, and 3 lemons yield about ½ cup juice
    \item \textbf{TrueLemon powder} significantly amplifies lemon brightness without added liquid
    \item Fresh \textbf{lemon zest} is essential for aromatic oils and complexity
    \item Use the finest grater for \textbf{zest} to avoid bitter white pith
\end{itemize}

\subsection*{Preparation Tips}
\begin{itemize}
    \item Strain \textbf{raspberry} seeds thoroughly; any seeds in the reduction will clog piping tip
    \item Test reduction consistency when cool—it should be thick like honey but still flow smoothly through piping tip
    \item If reduction is too thick after cooling, warm slightly and thin with 1~tsp. water at a time
    \item Press crust very firmly and evenly; uneven thickness causes uneven baking
    \item Dock crust thoroughly to prevent bubbling during baking
    \item Don't underbake the crust; edges should be golden for structural integrity
    \item Stir curd constantly to prevent curdling; use silicone spatula to scrape sides
    \item Watch for \textit{170°F} on thermometer or coat-the-spoon consistency
    \item Strain while curd is hot for easiest flow through sieve
    \item Pour curd onto hot crust immediately after straining
    \item Pipe \textbf{raspberry reduction} immediately after pouring lemon curd, before it begins to set
    \item Use thin, elegant lines or loops—less is more for visual impact
    \item The \textbf{raspberry} will deepen to burgundy during baking; this is normal and beautiful
    \item The filling will continue to set as it cools; slight jiggle is correct
    \item Clean knife between cuts for neat edges
    \item Add \textbf{powdered sugar} and \textbf{salt} just before serving to prevent dissolving
\end{itemize}

\subsection*{Make Ahead \& Storage}
\begin{itemize}
    \item \textbf{Raspberry reduction} can be made up to \textit{3~days} ahead; store covered in refrigerator and bring to room temperature before using
    \item Bars must cool completely and chill at least \textit{3~hours} before cutting
    \item Best made a day ahead; flavors meld and texture improves overnight
    \item Store covered in refrigerator for up to \textit{5~days}; bring to cool room temperature before serving for best texture (\textit{15-20~minutes})
    \item Can be frozen unfrosted for up to \textit{2~months}; thaw in refrigerator overnight
    \item For meal prep, cut and store individually wrapped in refrigerator
\end{itemize}

\subsection*{Serving Suggestions}
\begin{itemize}
    \item Serve as elegant finger food dessert at room temperature
    \item Pair with hot tea, coffee, or sparkling wine
    \item Garnish individual servings with fresh mint, candied lemon peel, or fresh raspberries
    \item Serve alongside fresh berries or whipped cream for plated dessert
    \item The \textbf{flaky salt} provides crucial sweet-savory contrast
\end{itemize}

\end{multicols}
}

\end{document}