\documentclass[11pt,letterpaper]{article}
\usepackage{fontspec}
\usepackage{tocloft} % For dotted lines
\usepackage{multicol}
\usepackage[left=1.5in,right=1.5in,top=1in,bottom=1in]{geometry}
\setmainfont[Scale=1.3,AutoFakeBold=1.5,AutoFakeSlant=0.3]{Doves Type}


\title{Pumpkin Pie}
\author{Paula Deen}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\section*{Ingredients}
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\noindent
    Frozen Pie Crusts \dotfill 2 \\
    Cream Cheese \dotfill 8 oz. \\
    Canned Pumpkin \dotfill 2 cups \\
    Sugar \dotfill 1 cup \\
	Salt \dotfill ¼ tsp. \\
	1 egg, plus 2 yolks \dotfill 3 eggs  \\ 
	\columnbreak
	Heavy Cream \dotfill ½ cup \\
	Milk \dotfill ½ cup \\
	Butter (melted) \dotfill ¼ cup \\
	Vanilla Extract \dotfill 1 tsp. \\
	Cinnamon, ground \dotfill ½ tsp. \\
	Ginger, ground \dotfill ½ tsp. \\
	Whipped Cream \dotfill 1 cup \\
\end{multicols}

\section*{Directions}

\noindent
Preheat Oven to 350°F ---
Thaw \textbf{pie crusts} about \textbf{15 minutes} at room temperature ---
Lightly beat eggs
\subsection*{Pie Crusts}

\begin{enumerate}
	\item Fit a piece of aluminum foil to cover the inside of the shell completely. Fill the shell to the edges with dried beans.
	\item Bake the \textbf{pie crusts} at \textbf{350°F} for \textbf{10 minutes}, then remove the beans and foil and bake for another \textbf{5-10 minutes} until dried and beginning to color. Keep warm.
\end{enumerate}

\subsection*{Filling}
\begin{enumerate}
	\item In a large mixing bowl beat the \textbf{cream cheese} with a hand mixer.
	\item Add the \textbf{pumpkin}, then beat until combined.
	\item Add the \textbf{sugar} and \textbf{salt}, then beat until combined.
	\item Add the \textbf{eggs and yolks}, \textbf{milk}, \textbf{cream}, and \textbf{butter}, then beat until combined.
	\item Add the \textbf{vanilla}, \textbf{cinnamon}, and \textbf{ginger}, then beat until combined.
	\item Pour the filling into the pie crusts and loosely wrap the edges with aluminum foil to prevent burning.
	\item Bake for \textbf{40 minutes} at \textbf{350°F}
	\item Remove foil from edges and bake for \textbf{10 minutes}, or until the center is set.
	\item Cool on a wire rack until room temperature. Slice and serve topped with \textbf{whipped cream}.
\end{enumerate}

\end{document}
